---
title: "Two-symbiont model simulations"
author: "Ross Cunning"
date: "2/19/2018"
output: html_document
---

```{r setup, include=FALSE}
# Set kintr options
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

# Load packages
library(coRal)
library(plotrix)
library(scales)
require(foreach)
require(parallel)
require(doParallel)
library(tidyverse)
```

```{r define_functions, eval=T, include=F}
# Define function for plotting S/H for two-symbiont simulations
plot_2sh <- function(run) {
  nsym <- ifelse("list" %in% class(run$S), length(run$S), 1)
  if (nsym > 1) {
    totSH <- rowSums(sapply(run$S, "[[", 2))/run$H$H
  } else {
    totSH <- run$S$S/run$H$H
  }
  plot(time, totSH, ylim=c(0, max(totSH*1.2)), type="l",
       xlab="Time (days)", ylab="S:H ratio")
  if (nsym > 1) for (i in 1:nsym) {
    lines(run$S[[i]]$S/run$H$H ~ time, col=cols[i])
  }
  # Find which pars are different btw symbionts and annotate plot
  d <- names(which(lapply(pars, function(x) length(unique(x))!=1)==T))
  d <- d[!d %in% "initS"]
  df <- data.frame(pars[d])
  text(x=100,y=par("usr")[4]*0.90,paste0(colnames(df), collapse="    "), pos=3)
  text(x=100,y=par("usr")[4]*0.85,paste0(df[1,], collapse="       "), pos=3, col="blue")
  text(x=100,y=par("usr")[4]*0.80,paste0(df[2,], collapse="       "), pos=3, col="red")
  # Annotate S:H ratios
  at <- c(1,365,730)
  s1h <- round(with(run, (S[[1]]$S/H$H)[H$time %in% at]), 3)
  text(at, s1h, s1h, col="blue", cex=0.7)
  s2h <- round(with(run, (S[[2]]$S/H$H)[H$time %in% at]), 3)
  text(at, s2h, s2h, col="red", cex=0.7)
}
cols=c("blue", "red")

plot_2sh <- function(run) with(run, {
  plot(time, env.L, type="l", col=scales::alpha("gold", 0.5), axes=F, ylim=c(0, 50), ylab="", xlab="")
  axis(side=4)
  par(new=T)
  plot(time, (S.1+S.2)/H, ylim=c(0, max((S.1+S.2)/H*1.1)), type="l", ylab="S/H", xlab="Days")
  lines(S.1/H ~ time, col="blue")
  lines(S.2/H ~ time, col="red")
  legend("topright", legend=c("sensitive", "tolerant"), col=c("blue", "red"), lty=1, bty="n")
})
```

# Parameterize sensitive and tolerant symbionts
What we know about "tolerant" symbionts:  

* Lower photosynthetic rates
    + Reduce jCPm from 2.8 to 1.0
* Lower ROS production
    + Increase kROS from 80 to 250
* Lower growth rates
    + Reduce jSGm from 0.25 to 0.15
    

```{r parameterize_syms, fig.height=5, fig.width=5}
# Sensitive symbiont -- default max. photosynthetic rate and ROS production
ssym <- def_pars(nsym=1)
ssym$jCPm <- 2.8; ssym$kROS <- 80; ssym$jSGm <- 0.25
ssympi <- sym_PI(ssym, draw=FALSE)
# Tolerant symbiont -- lower max. photosynthetic rate, lower ROS production
tsym <- def_pars(nsym=1)
tsym$jCPm <- 1.0; tsym$kROS <- 250; tsym$jSGm <- 0.15
tsympi <- sym_PI(tsym, draw=FALSE)

# Plot Photosynthesis and ROS production for each symbiont as a function of irradiance
par(mfcol=c(2,2), mar=c(2.1,2.1,1,1), mgp=c(1.1,0.1,0), tcl=-0.2, cex.axis=0.6, cex.lab=0.8)
plot(ssympi$jCP/ssym$yCL ~ ssympi$jL, type="l", lwd=1,
     xlab="Irradiance (mol photons/C-mol S/d)",
     ylab="P gross (mol C/C-mol S/d)", ylim=c(0,17),
     main="Sensitive symbiont", col.main="blue")
plot(ssympi$cROS ~ ssympi$jL, type="l", lwd=1,
     xlab="Irradiance (mol photons/C-mol S/d)",
     ylab="ROS (relative)", ylim=c(1,3.2))
plot(tsympi$jCP/tsym$yCL ~ tsympi$jL, type="l", lwd=1,
     xlab="Irradiance (mol photons/C-mol S/d)",
     ylab="P gross (mol C/C-mol S/d)", ylim=c(0,17),
     main="Tolerant symbiont", col.main="red")
plot(tsympi$cROS ~ tsympi$jL, type="l", lwd=1,
     xlab="Irradiance (mol photons/C-mol S/d)",
     ylab="ROS (relative)", ylim=c(1,3.2))
```

PI and ROS production curves are consistent with expectations of a tolerant symbiont: maximum photosynthetic rate is reduced, but photoinhibition and ROS production are reduced at high light levels.
But what is their behavior when we put these symbionts into a coral host?

# Compare seasonal dynamics with either sensitive or tolerant symbiont
```{r seasonal, fig.width=5, fig.height=5}
# Define simulation environment (seasonal fluctuation in light)
time <- seq(1,365,0.1)
env <- init_env(time=time, X=c(2e-7,2e-7,0), N=c(1e-7,1e-7,0), L=c(30,15,3))

# Run simulations with sensitive or tolerant symbiont
run_s_s <- run_coral(time=time, env=env, pars=replace(ssym, "initS", 0.15))
run_s_t <- run_coral(time=time, env=env, pars=replace(tsym, "initS", 0.22))

# Plot
par(mfcol=c(3,2), mar=c(1.2,3,1,1), mgp=c(1.5,0.2,0), tcl=-0.2, cex.axis=1, cex.lab=1.2)
with(run_s_s, plot(env.L ~ time, col="gold", type="l", ylim=c(0, 50)))
title(main="Sensitive symbiont", col.main="blue")
with(run_s_s, plot(S/H ~ time, type="l", ylim=c(0,0.40)))
with(run_s_s, plot(dH.Hdt ~ time, type="l", ylim=c(0,0.04)))
with(run_s_t, plot(env.L ~ time, col="gold", type="l", ylim=c(0, 50)))
title(main="Tolerant symbiont", col.main="red")
with(run_s_t, plot(S/H ~ time, type="l", ylim=c(0,0.40)))
with(run_s_t, plot(dH.Hdt ~ time, type="l", ylim=c(0,0.04)))

# Calculate average difference in S/H ratio and host growth
mean(with(run_s_t, S/H) / with(run_s_s, S/H))  # Tolerant symbiont 1.5x higher S/H (annual mean)
mean(with(run_s_s, dH.Hdt) / with(run_s_t, dH.Hdt))  # Coral with sensitive symbiont grows 13% faster (annual mean)
```

Behavior is consistent with expectations: coral with tolerant symbiont has higher S/H ratio but grows slower than coral with sensitive symbiont. What about under stressful conditions (very high light levels)?

### Increase summertime maximum light to stressful levels
```{r bleaching, fig.width=5, fig.height=5}
# Define simulation environment (seasonal fluctuation in light)
time <- seq(1,365,0.1)
env <- init_env(time=time, X=c(2e-7,2e-7,0), N=c(1e-7,1e-7,0), L=c(50,15,3))

# Run simulations with sensitive or tolerant symbiont
run_s_s <- run_coral(time=time, env=env, pars=replace(ssym, "initS", 0.15))
run_s_t <- run_coral(time=time, env=env, pars=replace(tsym, "initS", 0.22))

# Plot
par(mfcol=c(3,2), mar=c(1.2,3,1,1), mgp=c(1.5,0.2,0), tcl=-0.2, cex.axis=1, cex.lab=1.2)
with(run_s_s, plot(env.L ~ time, col="gold", type="l", ylim=c(0, 50)))
title(main="Sensitive symbiont", col.main="blue")
with(run_s_s, plot(S/H ~ time, type="l", ylim=c(0,0.40)))
with(run_s_s, plot(dH.Hdt ~ time, type="l", ylim=c(0,0.04)))
with(run_s_t, plot(env.L ~ time, col="gold", type="l", ylim=c(0, 50)))
title(main="Tolerant symbiont", col.main="red")
with(run_s_t, plot(S/H ~ time, type="l", ylim=c(0,0.40)))
with(run_s_t, plot(dH.Hdt ~ time, type="l", ylim=c(0,0.04)))
```

Coral with sensitive symbiont bleaches, coral with tolerant symbiont does not.
What if both symbionts are present -- does shuffling occur?

# Test symbiont shuffling
```{r shuffling, eval=T}
# Get default parameters for two symbionts
pars <- def_pars(nsym=2)

# Make symbiont 2 have lower jCPm and higher kROS (i.e., tolerant symbiont)
pars$jCPm[2] <- 1.0
pars$kROS[2] <- 250
pars$jSGm[2] <- 0.15

# Make symbiont 2 start with very low biomass
pars$initS[1:2] <- c(0.2, 0.001)

# Define high light-stress environment for simulation
time <- seq(1,1000,0.1)
env <- init_env(time=time, X=c(2e-7,2e-7,0), N=c(1e-7,1e-7,0), L=c(20,15,4))

# Run simulation
run3 <- run_coral(time=time, env=env, pars=pars)

# Plot results
par(mfrow=c(1,1), mar=c(3,3,1,3), mgp=c(1.75,0.5,0))
plot_2sh(run3)
```

Yes, shuffling takes place, followed by reversion to sensitive symbiont.
How long does it take a coral with 99% tolerant symbiont to revert to 99% sensitive symbiont?

```{r loss1, eval=T}
# Get default parameters for two symbionts
pars <- def_pars(nsym=2)

# Make symbiont 2 have lower jCPm and higher kROS (i.e., tolerant symbiont)
pars$jCPm[2] <- 1.0
pars$kROS[2] <- 250
pars$jSGm[2] <- 0.15

# Start with 99% tolerant, 1% sensitive symbiont
pars$initS[1:2] <- c(0.002, 0.198)

# Define high light-stress environment for simulation
time <- seq(1,3650,0.1)
env <- init_env(time=time, X=c(2e-7,2e-7,0), N=c(1e-7,1e-7,0), L=c(30,10,3))

# Run simulation
run3 <- run_coral(time=time, env=env, pars=pars)

# Plot results
par(mar=c(3,3,1,3), mgp=c(1.75,0.5,0))
plot_2sh(run3)
```

Tolerant symbiont is gradually lost from the coral over about 15 years.

```{r loss2, eval=T}
# Get default parameters for two symbionts
pars <- def_pars(nsym=2)

# Make symbiont 2 have lower jCPm and higher kROS (i.e., tolerant symbiont)
pars$jCPm[2] <- 1.0
pars$kROS[2] <- 250
pars$jSGm[2] <- 0.15

# Start with 99% tolerant, 1% sensitive symbiont
pars$initS[1:2] <- c(0.002, 0.198)

# Define high light-stress environment for simulation
time <- seq(1,3650,0.1)
env <- init_env(time=time, X=c(2e-7,2e-7,0), N=c(1e-7,1e-7,0), L=c(20,20,0))

# Run simulation
run3 <- run_coral(time=time, env=env, pars=pars)

# Plot results
par(mar=c(3,3,1,3), mgp=c(1.75,0.5,0))
plot_2sh(run3)
```

Tolerant symbiont is lost in about 5 years at constant, intermediate light level. The two simulations involve the same mean light level, but variance is different. Variable environmental conditions serve to maintain symbiont diversity. 

### What sets of conditions favor tolerant vs. sensitive symbiont?
```{r competition}
# Get default parameters for two symbionts
pars <- def_pars(nsym=2)

# Make symbiont 2 have lower jCPm and higher kROS (i.e., tolerant symbiont)
pars$jCPm[2] <- 1.0
pars$kROS[2] <- 250
pars$jSGm[2] <- 0.15
pars$initS[1:2] <- 0.5

# Define environmental time and L and N gradients to test symbiont competition
time <- seq(0,300,0.1)
df <- expand.grid(L=seq(0, 40, 5), N=seq(1e-7, 1e-6, 1e-7))
#df <- as_tibble(df)

# Initialize environment for each set of L and N
#df$env <- apply(df, 1, function(x) init_env(time=time, L=c(x[1],x[1],0), N=c(x[2],x[2],0), X=c(1e-7,1e-7,0)))
  
# Set up cluster for parallel processing
cl <- makeCluster(detectCores())  # Initiate cluster
registerDoParallel(cl)
  
# Run simulations in parallel for each combination of "at" values
start <- proc.time()  # Start timer...
# Calculate steady states...
steady_states <- foreach(i=1:nrow(df), .combine='rbind', .packages='dplyr') %dopar% {
  env <- coRal::init_env(time=time, L=c(df[i,"L"],df[i,"L"],0), N=c(df[i,"N"],df[i,"N"],0), X=c(0,0,0))
  run <- coRal::run_coral(time=time, env=env, pars=pars)
  gr <- last(run$dH.Hdt)
  dom <- ifelse(last(run$S.1/run$S.2) > 1, "S1", "S2")
  list(gr=gr, dom=dom)
}
stopCluster(cl)  # Stop cluster
print(proc.time() - start)  # Print time elapsed if runtime==T

df <- cbind(df, steady_states, row.names=NULL)
df$dom[which(df$gr < 0)] <- ""
df

# Show dominant symbiont as a function of L and N
res <- spread(df[, c("L", "N", "dom")], N, dom)
res

head(df)
plot(NA, xlim=c(0, max(df$N)), ylim=c(0, max(df$L)), xlab="DIN", ylab="Light")
text(df$N, df$L, df$dom, col=c("white", "blue", "red")[factor(as.character(df$dom))])
```


```{r competition2}
# Get default parameters for four symbionts
pars <- def_pars(nsym=4)

# Make symbionts different
pars$jCPm[1:4] <- c(2.8, 2.0, 1.2, 2.8)
pars$kROS[1:4] <- c(80, 160, 240, 100)
pars$jSGm[1:4] <- c(0.25, 0.20, 0.15, 0.30)
pars$initS[1:4] <- 0.1
pars$nNS[1:4] <- c(0.13, 0.12, 0.11, 0.14)

# Define environmental time and L and N gradients to test symbiont competition
time <- seq(0,100,0.1)
df <- expand.grid(L=seq(0, 40, 5), N=seq(1e-7, 1e-6, 1e-7))
#df <- as_tibble(df)

# Initialize environment for each set of L and N
#df$env <- apply(df, 1, function(x) init_env(time=time, L=c(x[1],x[1],0), N=c(x[2],x[2],0), X=c(1e-7,1e-7,0)))
  
# Set up cluster for parallel processing
cl <- makeCluster(detectCores())  # Initiate cluster
registerDoParallel(cl)
  
# Run simulations in parallel for each combination of "at" values
start <- proc.time()  # Start timer...
# Calculate steady states...
steady_states <- foreach(i=1:nrow(df), .combine='rbind', .packages='dplyr') %dopar% {
  env <- coRal::init_env(time=time, L=c(df[i,"L"],df[i,"L"],0), N=c(df[i,"N"],df[i,"N"],0), X=c(0,0,0))
  run <- coRal::run_coral(time=time, env=env, pars=pars)
  gr <- last(run$dH.Hdt)
  dom <- names(which.max(run[nrow(run), grep("^S..$", colnames(run))]))
  list(gr=gr, dom=dom)
}
stopCluster(cl)  # Stop cluster
print(proc.time() - start)  # Print time elapsed if runtime==T

df <- cbind(df, steady_states, row.names=NULL)
df$dom[which(df$gr < 0)] <- ""
df

# Show dominant symbiont as a function of L and N
res <- spread(df[, c("L", "N", "dom")], N, dom)
res

head(df)
plot(NA, xlim=c(0, max(df$N)), ylim=c(0, max(df$L)), xlab="DIN", ylab="Light")
text(df$N, df$L, df$dom, col=rainbow(6)[factor(as.character(df$dom))])
```


Is temporal environmental variability required to maintain symbiont diversity? Under constant environment, will always go toward >99% of one symbiont?
