---
title: "Investigating a special case of shuffling in a constant environment"
author: "Ross Cunning and Alexandra Brown"
date: "5/6/2020"
output: html_document
---

```{r}
#Set kintr options
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, fig.width=8, fig.height=8)

library(coRal)
library(foreach)
library(parallel)
library(doParallel)
library(plot.matrix)
library("RColorBrewer")
library("viridis")

options(repr.plot.res=240)
```
```{r, cache = TRUE}
# one-symbiont parameters
pars1 <- def_pars(nsym=1)
pars1$initS <- 1e-4

# two-symbiont parameters
pars2 <- def_pars(nsym=2)
pars2$jCPm[2] <- 1.0
pars2$kROS[2] <- 250
pars2$jSGm[2] <- 0.15
pars2$initS[1:2] <- c(0.5e-4, 0.5e-4)

# run simulations for 23000 days
time<-seq(1, 3000, 0.1)

# draw sets of parameter values randomly
# hopefully this will speed things up compared to looking over a grid

draws = 10000; #2400; # number of sets of random parameter combinations to look over

search_params <- data.frame("L" = runif(draws, 0, 40),       # Light, choose values between 0 and 40
                            "N" = runif(draws, 0, 4e-6),     # DIN, choose values between 0 and 4e-6
                            "X" = runif(draws, 0, 4e-7),     # Food, choose values between 0 and 4e07
                            "kCO2" = runif(draws, 10, 50))   # kCO2 choose values between 10 and 50

# set up for parallel run
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

# start the timer
start <- proc.time()


# results will hold the parameter values tested as well as whether the tolerant symbiont "rescued"
# the sensitive symbiont at each parameter value

results <- foreach(i=1:nrow(search_params), .combine='rbind', .packages='dplyr') %dopar% {

    # Set up the environmental conditions
    env <- coRal::init_env(time=time, L=c(search_params[i, "L"], search_params[i, "L"], 0),
                           N=c(search_params[i, "N"], search_params[i, "N"], 0), X=c(search_params[i, "X"], search_params[i, "X"], 0))

    # simulate dynamics with just the sensitive symbiont
    run_1symb <- coRal::run_coral(time=time, env=env, pars=replace(pars1, "kCO2", search_params[i, "kCO2"]))

    # initialize rescue; will be TRUE if the tolerant symbiont rescued the sensitive
    rescue <- FALSE

    # initialize reason; will give the reason for lack of rescue if rescue does not occur
    # reason = "S_lives" -> host recovers with sensitive symbiont alone; does not need to be rescued by tolerant
    # reason = "T_dies" -> tolerant symbiont unable to rescue host
    # reason = "T_dominates" -> tolerant symbiont permits host recovery while sensitive does not, but tolerant dominates post-recovery
    # reason = "rescue" -> rescue occurred
    reason <- "S_lives"

    # if the coral can achieve positive growth with just the sensitive symbiont, the sensitive symbiont doesn't need to be rescued
    # only investigate the two-symbiont case if host growth is negative or 0 at the end of the simulation

    if (run_1symb$dH.Hdt[length(run_1symb$dH.Hdt)] <= 0) {


        run_2symb <- coRal::run_coral(time=time, env=env, pars=replace(pars2, "kCO2", search_params[i, "kCO2"]))

        # if the coral didn't achieve positive growth with both symbionts, then rescue definitely didn't happen
        # set reason to "T_dies" in case this is the case (we'll change it later if it isn't)
        reason <- "T_dies"

        # only further investigate the case where host growth is positive at the end of the simulation

        if (run_2symb$dH.Hdt[length(run_2symb$dH.Hdt)] > 0) {

            # the sensitive symbiont (S1) has been rescued if it now has higher biomass than the tolerant symbiont (S2)
            # set reason to "T_dominates" for now because this is what must have happened if rescue did not occur
            reason <- "T_dominates"

            if (run_2symb$S.1[length(run_2symb$S.1)] > run_2symb$S.2[length(run_2symb$S.2)]) {

                rescue <- TRUE
                reason <- "rescue"
            }
        }
    }

    # return the parameters and whether rescue was successful or not
    list("L"=search_params[i, "L"], "N"=search_params[i, "N"], "X"=search_params[i, "X"],
    "kCO2"=search_params[i, "kCO2"], "rescue"=rescue, "reason"=reason)
}

stopCluster(cl) # stop the cluster

# print time this took
print("Simulation took")
print(proc.time() - start)

# store results in dataframe
#(named rescue_jCPm_1 for comparison with the case where the tolerant symbiont has jCPm = 2.8)
rescue_jCPm_1 <- data.frame(results, row.names=NULL)

```

```{r}
sum(rescue_jCPm_1$rescue==TRUE)/nrow(rescue_jCPm_1)

sum(rescue_jCPm_1$reason=="S_lives")/nrow(rescue_jCPm_1)

sum(rescue_jCPm_1$reason=="T_dies")/nrow(rescue_jCPm_1)

sum(rescue_jCPm_1$reason=="T_dominates")/nrow(rescue_jCPm_1)
```

```{r}
par(mfrow=c(2, 3), pty="s")

#plot(rescue_jCPm_1[,"N"], rescue_jCPm_1[,"L"], main="Light vs DIN", xlab="N", ylab="L")
#points(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19)
plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
    main="Light vs DIN", xlab="N", ylab="L", xlim=c(0, 4e-6), ylim=c(0, 40))


#plot(rescue_jCPm_1[,"X"], rescue_jCPm_1[,"L"], main="Light vs Food", xlab="X", ylab="L")
#points(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19)
plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
     main="Light vs Food", xlab="X", ylab="L", xlim=c(0, 4e-07), ylim=c(0, 40))

plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"kCO2"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
     main="Light vs kCO2", xlab="kCO2", ylab="L", xlim=c(10, 50), ylim=c(0, 40))

plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
     main="DIN vs Food", xlab="Food", ylab="DIN", xlim=c(0, 4e-7), ylim=c(0, 4e-6))

plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"kCO2"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
     main="DIN vs kCO2", xlab="kCO2", ylab="DIN", xlim=c(10, 50), ylim=c(0, 4e-6))

plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"kCO2"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
     main="Food vs kCO2", xlab="kCO2", ylab="Food", xlim=c(10, 50), ylim=c(0, 4e-7))


png("env_regular_params.png")
par(mfrow=c(2, 3), pty="s")

#plot(rescue_jCPm_1[,"N"], rescue_jCPm_1[,"L"], main="Light vs DIN", xlab="N", ylab="L")
#points(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19)
plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
    main="Light vs DIN", xlab="N", ylab="L", xlim=c(0, 4e-6), ylim=c(0, 40))


#plot(rescue_jCPm_1[,"X"], rescue_jCPm_1[,"L"], main="Light vs Food", xlab="X", ylab="L")
#points(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19)
plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
     main="Light vs Food", xlab="X", ylab="L", xlim=c(0, 4e-07), ylim=c(0, 40))

plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"kCO2"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
     main="Light vs kCO2", xlab="kCO2", ylab="L", xlim=c(10, 50), ylim=c(0, 40))

plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
     main="DIN vs Food", xlab="Food", ylab="DIN", xlim=c(0, 4e-7), ylim=c(0, 4e-6))

plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"kCO2"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
     main="DIN vs kCO2", xlab="kCO2", ylab="DIN", xlim=c(10, 50), ylim=c(0, 4e-6))

plot(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"kCO2"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], pch=19, col=rgb(0, 0, 1, alpha=0.1),
     main="Food vs kCO2", xlab="kCO2", ylab="Food", xlim=c(10, 50), ylim=c(0, 4e-7))
dev.off()



png("env_regular_params_S_lives.png")
par(mfrow=c(2, 3), pty="s")

#plot(rescue_jCPm_1[,"N"], rescue_jCPm_1[,"L"], main="Light vs DIN", xlab="N", ylab="L")
#points(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19)
plot(rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","N"], rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","L"], pch=19, col=rgb(1, 0, 0, alpha=0.01),
        main="Light vs DIN", xlab="N", ylab="L", xlim=c(0, 4e-6), ylim=c(0, 40))

#plot(rescue_jCPm_1[,"X"], rescue_jCPm_1[,"L"], main="Light vs Food", xlab="X", ylab="L")
#points(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19)
plot(rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","X"], rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","L"], pch=19, col=rgb(1, 0, 0, alpha=0.01),
     main="Light vs Food", xlab="X", ylab="L", xlim=c(0, 4e-07), ylim=c(0, 40))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","kCO2"], rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","L"], pch=19, col=rgb(1, 0, 0, alpha=0.01),
     main="Light vs kCO2", xlab="kCO2", ylab="L", xlim=c(10, 50), ylim=c(0, 40))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","X"], rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","N"], pch=19, col=rgb(1, 0, 0, alpha=0.01),
     main="DIN vs Food", xlab="Food", ylab="DIN", xlim=c(0, 4e-7), ylim=c(0, 4e-6))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","kCO2"], rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","N"], pch=19, col=rgb(1, 0, 0, alpha=0.01),
     main="DIN vs kCO2", xlab="kCO2", ylab="DIN", xlim=c(10, 50), ylim=c(0, 4e-6))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","kCO2"], rescue_jCPm_1[rescue_jCPm_1$reason=="S_lives","X"], pch=19, col=rgb(1, 0, 0, alpha=0.01),
     main="Food vs kCO2", xlab="kCO2", ylab="Food", xlim=c(10, 50), ylim=c(0, 4e-7))

dev.off()


png("env_regular_params_T_dies.png")
par(mfrow=c(2, 3), pty="s")

#plot(rescue_jCPm_1[,"N"], rescue_jCPm_1[,"L"], main="Light vs DIN", xlab="N", ylab="L")
#points(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19)
plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","N"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","L"], pch=19, col=rgb(0, 1, 0, alpha=0.1),
        main="Light vs DIN", xlab="N", ylab="L", xlim=c(0, 4e-6), ylim=c(0, 40))

#plot(rescue_jCPm_1[,"X"], rescue_jCPm_1[,"L"], main="Light vs Food", xlab="X", ylab="L")
#points(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19)
plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","X"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","L"], pch=19, col=rgb(0, 1, 0, alpha=0.1),
     main="Light vs Food", xlab="X", ylab="L", xlim=c(0, 4e-07), ylim=c(0, 40))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","kCO2"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","L"], pch=19, col=rgb(0, 1, 0, alpha=0.1),
     main="Light vs kCO2", xlab="kCO2", ylab="L", xlim=c(10, 50), ylim=c(0, 40))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","X"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","N"], pch=19, col=rgb(0, 1, 0, alpha=0.1),
     main="DIN vs Food", xlab="Food", ylab="DIN", xlim=c(0, 4e-7), ylim=c(0, 4e-6))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","kCO2"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","N"], pch=19, col=rgb(0, 1, 0, alpha=0.1),
     main="DIN vs kCO2", xlab="kCO2", ylab="DIN", xlim=c(10, 50), ylim=c(0, 4e-6))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","kCO2"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dies","X"], pch=19, col=rgb(0, 1, 0, alpha=0.1),
     main="Food vs kCO2", xlab="kCO2", ylab="Food", xlim=c(10, 50), ylim=c(0, 4e-7))

dev.off()

png("env_regular_params_T_dominates.png")
par(mfrow=c(2, 3), pty="s")

#plot(rescue_jCPm_1[,"N"], rescue_jCPm_1[,"L"], main="Light vs DIN", xlab="N", ylab="L")
#points(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"N"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19)
plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","N"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","L"], pch=19, col=rgb(0, 0, 0, alpha=1),
        main="Light vs DIN", xlab="N", ylab="L", xlim=c(0, 4e-6), ylim=c(0, 40))

#plot(rescue_jCPm_1[,"X"], rescue_jCPm_1[,"L"], main="Light vs Food", xlab="X", ylab="L")
#points(rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"X"], rescue_jCPm_1[rescue_jCPm_1$rescue==TRUE,"L"], pch=19)
plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","X"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","L"], pch=19, col=rgb(0, 0, 0, alpha=1),
     main="Light vs Food", xlab="X", ylab="L", xlim=c(0, 4e-07), ylim=c(0, 40))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","kCO2"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","L"], pch=19, col=rgb(0, 0, 0, alpha=1),
     main="Light vs kCO2", xlab="kCO2", ylab="L", xlim=c(10, 50), ylim=c(0, 40))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","X"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","N"], pch=19, col=rgb(0, 0, 0, alpha=1),
     main="DIN vs Food", xlab="Food", ylab="DIN", xlim=c(0, 4e-7), ylim=c(0, 4e-6))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","kCO2"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","N"], pch=19, col=rgb(0,0, 0, alpha=1),
     main="DIN vs kCO2", xlab="kCO2", ylab="DIN", xlim=c(10, 50), ylim=c(0, 4e-6))

plot(rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","kCO2"], rescue_jCPm_1[rescue_jCPm_1$reason=="T_dominates","X"], pch=19, col=rgb(0, 0, 0, alpha=1),
     main="Food vs kCO2", xlab="kCO2", ylab="Food", xlim=c(10, 50), ylim=c(0, 4e-7))

dev.off()

```
```

```{r}
par(mfrow=c(2, 2))

Light_data = data.frame(bins=seq(0, 40, 5), vals=NA)

for (i in 1:length(Light_data$bins)-1) {
    Light_data$vals[i] <- sum(with(rescue_jCPm_1, L >= Light_data$bins[i] & L < Light_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_jCPm_1, L >= Light_data$bins[i] & L < Light_data$bins[i+1]))
}

with(Light_data[-nrow(Light_data),], {
    plot(bins, vals, main="Light", xlab="L", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})


DIN_data = data.frame(bins=seq(0, 4e-6, 5e-7), vals=NA)

for (i in 1:length(DIN_data$bins)-1) {
    DIN_data$vals[i] <- sum(with(rescue_jCPm_1, N >= DIN_data$bins[i] & N < DIN_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_jCPm_1, N >= DIN_data$bins[i] & N < DIN_data$bins[i+1]))
}

with(DIN_data[-nrow(DIN_data),], {
    plot(bins, vals, main="DIN", xlab="N", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})



Food_data = data.frame(bins=seq(0, 4e-7, 5e-8), vals=NA)

for (i in 1:length(Food_data$bins)-1) {
    Food_data$vals[i] <- sum(with(rescue_jCPm_1, X >= Food_data$bins[i] & X < Food_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_jCPm_1, X >= Food_data$bins[i] & X < Food_data$bins[i+1]))
}

with(Food_data[-nrow(Food_data),], {
    plot(bins, vals, main="Food", xlab="X", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})



png("single_param_rescue_normal.png")
kCO2_data = data.frame(bins=seq(10, 50, 5), vals=NA)


for (i in 1:length(kCO2_data$bins)-1) {
    kCO2_data$vals[i] <- sum(with(rescue_jCPm_1, kCO2 >= kCO2_data$bins[i] & kCO2 < kCO2_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_jCPm_1, kCO2 >= kCO2_data$bins[i] & kCO2 < kCO2_data$bins[i+1]))
}

with(kCO2_data[-nrow(kCO2_data),], {
    plot(bins, vals, main="kCO2", xlab="kCO2", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})


    par(mfrow=c(2, 2))

    Light_data = data.frame(bins=seq(0, 40, 5), vals=NA)

    for (i in 1:length(Light_data$bins)-1) {
        Light_data$vals[i] <- sum(with(rescue_jCPm_1, L >= Light_data$bins[i] & L < Light_data$bins[i+1] & rescue==TRUE))/
        sum(with(rescue_jCPm_1, L >= Light_data$bins[i] & L < Light_data$bins[i+1]))
    }

    with(Light_data[-nrow(Light_data),], {
        plot(bins, vals, main="Light", xlab="L", ylab="fraction of tested values w/ rescue")
        lines(bins, vals)})


    DIN_data = data.frame(bins=seq(0, 4e-6, 5e-7), vals=NA)

    for (i in 1:length(DIN_data$bins)-1) {
        DIN_data$vals[i] <- sum(with(rescue_jCPm_1, N >= DIN_data$bins[i] & N < DIN_data$bins[i+1] & rescue==TRUE))/
        sum(with(rescue_jCPm_1, N >= DIN_data$bins[i] & N < DIN_data$bins[i+1]))
    }

    with(DIN_data[-nrow(DIN_data),], {
        plot(bins, vals, main="DIN", xlab="N", ylab="fraction of tested values w/ rescue")
        lines(bins, vals)})



    Food_data = data.frame(bins=seq(0, 4e-7, 5e-8), vals=NA)

    for (i in 1:length(Food_data$bins)-1) {
        Food_data$vals[i] <- sum(with(rescue_jCPm_1, X >= Food_data$bins[i] & X < Food_data$bins[i+1] & rescue==TRUE))/
        sum(with(rescue_jCPm_1, X >= Food_data$bins[i] & X < Food_data$bins[i+1]))
    }

    with(Food_data[-nrow(Food_data),], {
        plot(bins, vals, main="Food", xlab="X", ylab="fraction of tested values w/ rescue")
        lines(bins, vals)})




    kCO2_data = data.frame(bins=seq(10, 50, 5), vals=NA)


    for (i in 1:length(kCO2_data$bins)-1) {
        kCO2_data$vals[i] <- sum(with(rescue_jCPm_1, kCO2 >= kCO2_data$bins[i] & kCO2 < kCO2_data$bins[i+1] & rescue==TRUE))/
        sum(with(rescue_jCPm_1, kCO2 >= kCO2_data$bins[i] & kCO2 < kCO2_data$bins[i+1]))
    }

    with(kCO2_data[-nrow(kCO2_data),], {
        plot(bins, vals, main="kCO2", xlab="kCO2", ylab="fraction of tested values w/ rescue")
        lines(bins, vals)})
dev.off()
```


# jCPm = 2.8


```{r, cache=TRUE}
# one-symbiont parameters
pars1 <- def_pars(nsym=1)
pars1$initS <- 1e-4

# two-symbiont parameters
pars2 <- def_pars(nsym=2)
pars2$kROS[2] <- 250
pars2$jSGm[2] <- 0.15
pars2$initS[1:2] <- c(0.5e-4, 0.5e-4)

# run simulations for 23000 days
time<-seq(1, 3000, 0.1)

# draw sets of parameter values randomly
# hopefully this will speed things up compared to looking over a grid

draws = 10000; # number of sets of random parameter combinations to look over

search_params <- data.frame("L" = runif(draws, 0, 40),       # Light, choose values between 0 and 40
                            "N" = runif(draws, 0, 4e-6),     # DIN, choose values between 0 and 4e-6
                            "X" = runif(draws, 0, 4e-7),     # Food, choose values between 0 and 4e07
                            "kCO2" = runif(draws, 10, 50))   # kCO2 choose values between 10 and 50


# set up for parallel run
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

# start the timer
start <- proc.time()


# results will hold the parameter values tested as well as whether the tolerant symbiont "rescued"
# the sensitive symbiont at each parameter value

results_2.8 <- foreach(i=1:nrow(search_params), .combine='rbind', .packages='dplyr') %dopar% {

    # Set up the environmental conditions
    env <- coRal::init_env(time=time, L=c(search_params[i, "L"], search_params[i, "L"], 0),
                           N=c(search_params[i, "N"], search_params[i, "N"], 0), X=c(search_params[i, "X"], search_params[i, "X"], 0))

    # simulate dynamics with just the sensitive symbiont
    run_1symb <- coRal::run_coral(time=time, env=env, pars=replace(pars1, "kCO2", search_params[i, "kCO2"]))

    # initialize rescue; will be TRUE if the tolerant symbiont rescued the sensitive
    rescue <- FALSE

    # initialize reason; will give the reason for lack of rescue if rescue does not occur
    # reason = "S_lives" -> host recovers with sensitive symbiont alone; does not need to be rescued by tolerant
    # reason = "T_dies" -> tolerant symbiont unable to rescue host
    # reason = "T_dominates" -> tolerant symbiont permits host recovery while sensitive does not, but tolerant dominates post-recovery
    # reason = "rescue" -> rescue occurred
    reason <- "S_lives"

    # if the coral can achieve positive growth with just the sensitive symbiont, the sensitive symbiont doesn't need to be rescued
    # only investigate the two-symbiont case if host growth is negative or 0 at the end of the simulation

    if (run_1symb$dH.Hdt[length(run_1symb$dH.Hdt)] <= 0) {


        run_2symb <- coRal::run_coral(time=time, env=env, pars=replace(pars2, "kCO2", search_params[i, "kCO2"]))

        # if the coral didn't achieve positive growth with both symbionts, then rescue definitely didn't happen
        # set reason to "T_dies" in case this is the case (we'll change it later if it isn't)
        reason <- "T_dies"

        # only further investigate the case where host growth is positive at the end of the simulation

        if (run_2symb$dH.Hdt[length(run_2symb$dH.Hdt)] > 0) {

            # the sensitive symbiont (S1) has been rescued if it now has higher biomass than the tolerant symbiont (S2)
            # set reason to "T_dominates" for now because this is what must have happened if rescue did not occur
            reason <- "T_dominates"

            if (run_2symb$S.1[length(run_2symb$S.1)] > run_2symb$S.2[length(run_2symb$S.2)]) {

                rescue <- TRUE
                reason <- "rescue"
            }
        }
    }

    # return the parameters and whether rescue was successful or not
    list("L"=search_params[i, "L"], "N"=search_params[i, "N"], "X"=search_params[i, "X"],
    "kCO2"=search_params[i, "kCO2"], "rescue"=rescue, "reason"=reason)
}

stopCluster(cl) # stop the cluster

# print time this look
print("Simulation took")
print(proc.time() - start)

# store results in dataframe
rescue_jCPm_2.8 <- data.frame(results_2.8, row.names=NULL)

```

```{r}
sum(rescue_jCPm_2.8$rescue==TRUE)/nrow(rescue_jCPm_2.8)
```

```{r}
par(mfrow=c(2, 3), pty="s")

plot(rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"N"], rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"L"], pch=19,
    main="Light vs DIN", xlab="N", ylab="L", xlim=c(0, 4e-6), ylim=c(0, 40))

plot(rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"X"], rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"L"], pch=19,
     main="Light vs Food", xlab="X", ylab="L", xlim=c(0, 4e-07), ylim=c(0, 40))

plot(rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"kCO2"], rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"L"], pch=19,
     main="Light vs kCO2", xlab="kCO2", ylab="L", xlim=c(10, 50), ylim=c(0, 40))

plot(rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"X"], rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"N"], pch=19,
     main="DIN vs Food", xlab="Food", ylab="DIN", xlim=c(0, 4e-7), ylim=c(0, 4e-6))

plot(rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"kCO2"], rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"N"], pch=19,
     main="DIN vs kCO2", xlab="kCO2", ylab="DIN", xlim=c(10, 50), ylim=c(0, 4e-6))

plot(rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"kCO2"], rescue_jCPm_2.8[rescue_jCPm_2.8$rescue==TRUE,"X"], pch=19,
     main="Food vs kCO2", xlab="kCO2", ylab="Food", xlim=c(10, 50), ylim=c(0, 4e-7))
```

```{r}
par(mfrow=c(2, 2))

Light_data = data.frame(bins=seq(0, 40, 5), vals=NA)

for (i in 1:length(Light_data$bins)-1) {
    Light_data$vals[i] <- sum(with(rescue_jCPm_2.8, L >= Light_data$bins[i] & L < Light_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_jCPm_2.8, L >= Light_data$bins[i] & L < Light_data$bins[i+1]))
}

with(Light_data[-nrow(Light_data),], {
    plot(bins, vals, main="Light", xlab="L", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})


DIN_data = data.frame(bins=seq(0, 4e-6, 5e-7), vals=NA)

for (i in 1:length(DIN_data$bins)-1) {
    DIN_data$vals[i] <- sum(with(rescue_jCPm_2.8, N >= DIN_data$bins[i] & N < DIN_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_jCPm_2.8, N >= DIN_data$bins[i] & N < DIN_data$bins[i+1]))
}

with(DIN_data[-nrow(DIN_data),], {
    plot(bins, vals, main="DIN", xlab="N", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})



Food_data = data.frame(bins=seq(0, 4e-7, 5e-8), vals=NA)

for (i in 1:length(Food_data$bins)-1) {
    Food_data$vals[i] <- sum(with(rescue_jCPm_2.8, X >= Food_data$bins[i] & X < Food_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_jCPm_2.8, X >= Food_data$bins[i] & X < Food_data$bins[i+1]))
}

with(Food_data[-nrow(Food_data),], {
    plot(bins, vals, main="Food", xlab="X", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})




kCO2_data = data.frame(bins=seq(10, 50, 5), vals=NA)


for (i in 1:length(kCO2_data$bins)-1) {
    kCO2_data$vals[i] <- sum(with(rescue_jCPm_2.8, kCO2 >= kCO2_data$bins[i] & kCO2 < kCO2_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_jCPm_2.8, kCO2 >= kCO2_data$bins[i] & kCO2 < kCO2_data$bins[i+1]))
}

with(kCO2_data[-nrow(kCO2_data),], {
    plot(bins, vals, main="kCO2", xlab="kCO2", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})
```


# kNPQ = 123.1

```{r, cache=TRUE}
# one-symbiont parameters
pars1 <- def_pars(nsym=1)
pars1$initS <- 1e-4

# two-symbiont parameters
pars2 <- def_pars(nsym=2)
pars2$jCPm[2] <- 1
pars2$kROS[2] <- 250
pars2$jSGm[2] <- 0.15
pars2$kNPQ[2] <- 123.1
pars2$initS[1:2] <- c(0.5e-4, 0.5e-4)

# run simulations for 23000 days
time<-seq(1, 3000, 0.1)

# draw sets of parameter values randomly
# hopefully this will speed things up compared to looking over a grid

draws = 10000; # number of sets of random parameter combinations to look over

search_params <- data.frame("L" = runif(draws, 0, 40),       # Light, choose values between 0 and 40
                            "N" = runif(draws, 0, 4e-6),     # DIN, choose values between 0 and 4e-6
                            "X" = runif(draws, 0, 4e-7),     # Food, choose values between 0 and 4e07
                            "kCO2" = runif(draws, 10, 50))   # kCO2 choose values between 10 and 50


# set up for parallel run
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

# start the timer
start <- proc.time()


# results will hold the parameter values tested as well as whether the tolerant symbiont "rescued"
# the sensitive symbiont at each parameter value

results_kNPQ <- foreach(i=1:nrow(search_params), .combine='rbind', .packages='dplyr') %dopar% {

    # Set up the environmental conditions
    env <- coRal::init_env(time=time, L=c(search_params[i, "L"], search_params[i, "L"], 0),
                           N=c(search_params[i, "N"], search_params[i, "N"], 0), X=c(search_params[i, "X"], search_params[i, "X"], 0))

    # simulate dynamics with just the sensitive symbiont
    run_1symb <- coRal::run_coral(time=time, env=env, pars=replace(pars1, "kCO2", search_params[i, "kCO2"]))

    # initialize rescue; will be TRUE if the tolerant symbiont rescued the sensitive
    rescue <- FALSE

    # initialize reason; will give the reason for lack of rescue if rescue does not occur
    # reason = "S_lives" -> host recovers with sensitive symbiont alone; does not need to be rescued by tolerant
    # reason = "T_dies" -> tolerant symbiont unable to rescue host
    # reason = "T_dominates" -> tolerant symbiont permits host recovery while sensitive does not, but tolerant dominates post-recovery
    # reason = "rescue" -> rescue occurred
    reason <- "S_lives"

    # if the coral can achieve positive growth with just the sensitive symbiont, the sensitive symbiont doesn't need to be rescued
    # only investigate the two-symbiont case if host growth is negative or 0 at the end of the simulation

    if (run_1symb$dH.Hdt[length(run_1symb$dH.Hdt)] <= 0) {


        run_2symb <- coRal::run_coral(time=time, env=env, pars=replace(pars2, "kCO2", search_params[i, "kCO2"]))

        # if the coral didn't achieve positive growth with both symbionts, then rescue definitely didn't happen
        # set reason to "T_dies" in case this is the case (we'll change it later if it isn't)
        reason <- "T_dies"

        # only further investigate the case where host growth is positive at the end of the simulation

        if (run_2symb$dH.Hdt[length(run_2symb$dH.Hdt)] > 0) {

            # the sensitive symbiont (S1) has been rescued if it now has higher biomass than the tolerant symbiont (S2)
            # set reason to "T_dominates" for now because this is what must have happened if rescue did not occur
            reason <- "T_dominates"

            if (run_2symb$S.1[length(run_2symb$S.1)] > run_2symb$S.2[length(run_2symb$S.2)]) {

                rescue <- TRUE
                reason <- "rescue"
            }
        }
    }

    # return the parameters and whether rescue was successful or not
    list("L"=search_params[i, "L"], "N"=search_params[i, "N"], "X"=search_params[i, "X"],
    "kCO2"=search_params[i, "kCO2"], "rescue"=rescue, "reason"=reason)
}

stopCluster(cl) # stop the cluster

# print time this look
print("Simulation took")
print(proc.time() - start)

# store results in dataframe
rescue_kNPQ <- data.frame(results_kNPQ, row.names=NULL)

```

```{r}
sum(rescue_kNPQ$rescue==TRUE)/nrow(rescue_kNPQ)
```

```{r}
par(mfrow=c(2, 3), pty="s")

plot(rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"N"], rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"L"], pch=19,
    main="Light vs DIN", xlab="N", ylab="L", xlim=c(0, 4e-6), ylim=c(0, 40))

plot(rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"X"], rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"L"], pch=19,
     main="Light vs Food", xlab="X", ylab="L", xlim=c(0, 4e-07), ylim=c(0, 40))

plot(rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"kCO2"], rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"L"], pch=19,
     main="Light vs kCO2", xlab="kCO2", ylab="L", xlim=c(10, 50), ylim=c(0, 40))

plot(rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"X"], rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"N"], pch=19,
     main="DIN vs Food", xlab="Food", ylab="DIN", xlim=c(0, 4e-7), ylim=c(0, 4e-6))

plot(rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"kCO2"], rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"N"], pch=19,
     main="DIN vs kCO2", xlab="kCO2", ylab="DIN", xlim=c(10, 50), ylim=c(0, 4e-6))

plot(rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"kCO2"], rescue_kNPQ[rescue_kNPQ$rescue==TRUE,"X"], pch=19,
     main="Food vs kCO2", xlab="kCO2", ylab="Food", xlim=c(10, 50), ylim=c(0, 4e-7))
```

```{r}
par(mfrow=c(2, 2))

Light_data = data.frame(bins=seq(0, 40, 5), vals=NA)

for (i in 1:length(Light_data$bins)-1) {
    Light_data$vals[i] <- sum(with(rescue_kNPQ, L >= Light_data$bins[i] & L < Light_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_kNPQ, L >= Light_data$bins[i] & L < Light_data$bins[i+1]))
}

with(Light_data[-nrow(Light_data),], {
    plot(bins, vals, main="Light", xlab="L", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})


DIN_data = data.frame(bins=seq(0, 4e-6, 5e-7), vals=NA)

for (i in 1:length(DIN_data$bins)-1) {
    DIN_data$vals[i] <- sum(with(rescue_kNPQ, N >= DIN_data$bins[i] & N < DIN_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_kNPQ, N >= DIN_data$bins[i] & N < DIN_data$bins[i+1]))
}

with(DIN_data[-nrow(DIN_data),], {
    plot(bins, vals, main="DIN", xlab="N", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})



Food_data = data.frame(bins=seq(0, 4e-7, 5e-8), vals=NA)

for (i in 1:length(Food_data$bins)-1) {
    Food_data$vals[i] <- sum(with(rescue_kNPQ, X >= Food_data$bins[i] & X < Food_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_kNPQ, X >= Food_data$bins[i] & X < Food_data$bins[i+1]))
}

with(Food_data[-nrow(Food_data),], {
    plot(bins, vals, main="Food", xlab="X", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})




kCO2_data = data.frame(bins=seq(10, 50, 5), vals=NA)


for (i in 1:length(kCO2_data$bins)-1) {
    kCO2_data$vals[i] <- sum(with(rescue_kNPQ, kCO2 >= kCO2_data$bins[i] & kCO2 < kCO2_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_kNPQ, kCO2 >= kCO2_data$bins[i] & kCO2 < kCO2_data$bins[i+1]))
}

with(kCO2_data[-nrow(kCO2_data),], {
    plot(bins, vals, main="kCO2", xlab="kCO2", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})
```

# astar = 1.474

```{r, cache=TRUE}
# one-symbiont parameters
pars1 <- def_pars(nsym=1)
pars1$initS <- 1e-4

# two-symbiont parameters
pars2 <- def_pars(nsym=2)
pars2$jCPm[2] <- 1
pars2$kROS[2] <- 250
pars2$jSGm[2] <- 0.15
pars2$astar[2] <- 1.474
pars2$initS[1:2] <- c(0.5e-4, 0.5e-4)

# run simulations for 23000 days
time<-seq(1, 3000, 0.1)

# draw sets of parameter values randomly
# hopefully this will speed things up compared to looking over a grid

draws = 10000; # number of sets of random parameter combinations to look over

search_params <- data.frame("L" = runif(draws, 0, 40),       # Light, choose values between 0 and 40
                            "N" = runif(draws, 0, 4e-6),     # DIN, choose values between 0 and 4e-6
                            "X" = runif(draws, 0, 4e-7),     # Food, choose values between 0 and 4e07
                            "kCO2" = runif(draws, 10, 50))   # kCO2 choose values between 10 and 50


# set up for parallel run
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

# start the timer
start <- proc.time()


# results will hold the parameter values tested as well as whether the tolerant symbiont "rescued"
# the sensitive symbiont at each parameter value

results_astar <- foreach(i=1:nrow(search_params), .combine='rbind', .packages='dplyr') %dopar% {

    # Set up the environmental conditions
    env <- coRal::init_env(time=time, L=c(search_params[i, "L"], search_params[i, "L"], 0),
                           N=c(search_params[i, "N"], search_params[i, "N"], 0), X=c(search_params[i, "X"], search_params[i, "X"], 0))

    # simulate dynamics with just the sensitive symbiont
    run_1symb <- coRal::run_coral(time=time, env=env, pars=replace(pars1, "kCO2", search_params[i, "kCO2"]))

    # initialize rescue; will be TRUE if the tolerant symbiont rescued the sensitive
    rescue <- FALSE

    # initialize reason; will give the reason for lack of rescue if rescue does not occur
    # reason = "S_lives" -> host recovers with sensitive symbiont alone; does not need to be rescued by tolerant
    # reason = "T_dies" -> tolerant symbiont unable to rescue host
    # reason = "T_dominates" -> tolerant symbiont permits host recovery while sensitive does not, but tolerant dominates post-recovery
    # reason = "rescue" -> rescue occurred
    reason <- "S_lives"

    # if the coral can achieve positive growth with just the sensitive symbiont, the sensitive symbiont doesn't need to be rescued
    # only investigate the two-symbiont case if host growth is negative or 0 at the end of the simulation

    if (run_1symb$dH.Hdt[length(run_1symb$dH.Hdt)] <= 0) {


        run_2symb <- coRal::run_coral(time=time, env=env, pars=replace(pars2, "kCO2", search_params[i, "kCO2"]))

        # if the coral didn't achieve positive growth with both symbionts, then rescue definitely didn't happen
        # set reason to "T_dies" in case this is the case (we'll change it later if it isn't)
        reason <- "T_dies"

        # only further investigate the case where host growth is positive at the end of the simulation

        if (run_2symb$dH.Hdt[length(run_2symb$dH.Hdt)] > 0) {

            # the sensitive symbiont (S1) has been rescued if it now has higher biomass than the tolerant symbiont (S2)
            # set reason to "T_dominates" for now because this is what must have happened if rescue did not occur
            reason <- "T_dominates"

            if (run_2symb$S.1[length(run_2symb$S.1)] > run_2symb$S.2[length(run_2symb$S.2)]) {

                rescue <- TRUE
                reason <- "rescue"
            }
        }
    }

    # return the parameters and whether rescue was successful or not
    list("L"=search_params[i, "L"], "N"=search_params[i, "N"], "X"=search_params[i, "X"],
    "kCO2"=search_params[i, "kCO2"], "rescue"=rescue, "reason"=reason)
}

stopCluster(cl) # stop the cluster

# print time this look
print("Simulation took")
print(proc.time() - start)

# store results in dataframe
rescue_astar <- data.frame(results_astar, row.names=NULL)

```

```{r}
sum(rescue_astar$rescue==TRUE)/nrow(rescue_astar)
```

```{r}
par(mfrow=c(2, 3), pty="s")

plot(rescue_astar[rescue_astar$rescue==TRUE,"N"], rescue_astar[rescue_astar$rescue==TRUE,"L"], pch=19,
    main="Light vs DIN", xlab="N", ylab="L", xlim=c(0, 4e-6), ylim=c(0, 40))

plot(rescue_astar[rescue_astar$rescue==TRUE,"X"], rescue_astar[rescue_astar$rescue==TRUE,"L"], pch=19,
     main="Light vs Food", xlab="X", ylab="L", xlim=c(0, 4e-07), ylim=c(0, 40))

plot(rescue_astar[rescue_astar$rescue==TRUE,"kCO2"], rescue_astar[rescue_astar$rescue==TRUE,"L"], pch=19,
     main="Light vs kCO2", xlab="kCO2", ylab="L", xlim=c(10, 50), ylim=c(0, 40))

plot(rescue_astar[rescue_astar$rescue==TRUE,"X"], rescue_astar[rescue_astar$rescue==TRUE,"N"], pch=19,
     main="DIN vs Food", xlab="Food", ylab="DIN", xlim=c(0, 4e-7), ylim=c(0, 4e-6))

plot(rescue_astar[rescue_astar$rescue==TRUE,"kCO2"], rescue_astar[rescue_astar$rescue==TRUE,"N"], pch=19,
     main="DIN vs kCO2", xlab="kCO2", ylab="DIN", xlim=c(10, 50), ylim=c(0, 4e-6))

plot(rescue_astar[rescue_astar$rescue==TRUE,"kCO2"], rescue_astar[rescue_astar$rescue==TRUE,"X"], pch=19,
     main="Food vs kCO2", xlab="kCO2", ylab="Food", xlim=c(10, 50), ylim=c(0, 4e-7))
```

```{r}
par(mfrow=c(2, 2))

Light_data = data.frame(bins=seq(0, 40, 5), vals=NA)

for (i in 1:length(Light_data$bins)-1) {
    Light_data$vals[i] <- sum(with(rescue_astar, L >= Light_data$bins[i] & L < Light_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_astar, L >= Light_data$bins[i] & L < Light_data$bins[i+1]))
}

with(Light_data[-nrow(Light_data),], {
    plot(bins, vals, main="Light", xlab="L", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})


DIN_data = data.frame(bins=seq(0, 4e-6, 5e-7), vals=NA)

for (i in 1:length(DIN_data$bins)-1) {
    DIN_data$vals[i] <- sum(with(rescue_astar, N >= DIN_data$bins[i] & N < DIN_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_astar, N >= DIN_data$bins[i] & N < DIN_data$bins[i+1]))
}

with(DIN_data[-nrow(DIN_data),], {
    plot(bins, vals, main="DIN", xlab="N", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})



Food_data = data.frame(bins=seq(0, 4e-7, 5e-8), vals=NA)

for (i in 1:length(Food_data$bins)-1) {
    Food_data$vals[i] <- sum(with(rescue_astar, X >= Food_data$bins[i] & X < Food_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_astar, X >= Food_data$bins[i] & X < Food_data$bins[i+1]))
}

with(Food_data[-nrow(Food_data),], {
    plot(bins, vals, main="Food", xlab="X", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})




kCO2_data = data.frame(bins=seq(10, 50, 5), vals=NA)


for (i in 1:length(kCO2_data$bins)-1) {
    kCO2_data$vals[i] <- sum(with(rescue_astar, kCO2 >= kCO2_data$bins[i] & kCO2 < kCO2_data$bins[i+1] & rescue==TRUE))/
    sum(with(rescue_astar, kCO2 >= kCO2_data$bins[i] & kCO2 < kCO2_data$bins[i+1]))
}

with(kCO2_data[-nrow(kCO2_data),], {
    plot(bins, vals, main="kCO2", xlab="kCO2", ylab="fraction of tested values w/ rescue")
    lines(bins, vals)})
```


#Identifying combination of food and kCO2 values that produces the most instances of "rescue"
```{r}
# We're going to check a grid of all the parameter combinations here
rescue_grid <- cbind(expand.grid("Xmin"=seq(0, 3.5e-7, 5e-8), "kCO2min"=seq(10, 45, 5)),
      expand.grid("Xmax"=seq(5e-8, 4e-7, 5e-8), "kCO2max"=seq(15, 50, 5)))

rescue_grid$rescue_fraction <- rep(NA, nrow(rescue_grid))

for (i in 1:nrow(rescue_grid)) {
      rescue_grid[i, "rescue_fraction"] <- sum(with(rescue_jCPm_1,
            X >= rescue_grid[i, "Xmin"] & X < rescue_grid[i, "Xmax"] &
            kCO2 >= rescue_grid[i, "kCO2min"] & kCO2 < rescue_grid[i, "kCO2max"] &
            rescue==TRUE)) / sum(with(rescue_jCPm_1,
                  X >= rescue_grid[i, "Xmin"] & X < rescue_grid[i, "Xmax"] &
                  kCO2 >= rescue_grid[i, "kCO2min"] & kCO2 < rescue_grid[i, "kCO2max"]))
}

print(rescue_grid[rescue_grid$rescue_fraction == max(rescue_grid$rescue_fraction),])
```

## jCPm = 2.8

```{r}
# We're going to check a grid of all the parameter combinations here
rescue_grid <- cbind(expand.grid("Xmin"=seq(0, 3.5e-7, 5e-8), "kCO2min"=seq(10, 45, 5)),
      expand.grid("Xmax"=seq(5e-8, 4e-7, 5e-8), "kCO2max"=seq(15, 50, 5)))

rescue_grid$rescue_fraction <- rep(NA, nrow(rescue_grid))

for (i in 1:nrow(rescue_grid)) {
      rescue_grid[i, "rescue_fraction"] <- sum(with(rescue_jCPm_2.8,
            X >= rescue_grid[i, "Xmin"] & X < rescue_grid[i, "Xmax"] &
            kCO2 >= rescue_grid[i, "kCO2min"] & kCO2 < rescue_grid[i, "kCO2max"] &
            rescue==TRUE)) / sum(with(rescue_jCPm_2.8,
                  X >= rescue_grid[i, "Xmin"] & X < rescue_grid[i, "Xmax"] &
                  kCO2 >= rescue_grid[i, "kCO2min"] & kCO2 < rescue_grid[i, "kCO2max"]))
}

print(rescue_grid[rescue_grid$rescue_fraction == max(rescue_grid$rescue_fraction),])
```

## kNPQ

```{r}
# We're going to check a grid of all the parameter combinations here
rescue_grid <- cbind(expand.grid("Xmin"=seq(0, 3.5e-7, 5e-8), "kCO2min"=seq(10, 45, 5)),
      expand.grid("Xmax"=seq(5e-8, 4e-7, 5e-8), "kCO2max"=seq(15, 50, 5)))

rescue_grid$rescue_fraction <- rep(NA, nrow(rescue_grid))

for (i in 1:nrow(rescue_grid)) {
      rescue_grid[i, "rescue_fraction"] <- sum(with(rescue_kNPQ,
            X >= rescue_grid[i, "Xmin"] & X < rescue_grid[i, "Xmax"] &
            kCO2 >= rescue_grid[i, "kCO2min"] & kCO2 < rescue_grid[i, "kCO2max"] &
            rescue==TRUE)) / sum(with(rescue_kNPQ,
                  X >= rescue_grid[i, "Xmin"] & X < rescue_grid[i, "Xmax"] &
                  kCO2 >= rescue_grid[i, "kCO2min"] & kCO2 < rescue_grid[i, "kCO2max"]))
}

print(rescue_grid[rescue_grid$rescue_fraction == max(rescue_grid$rescue_fraction),])
```

## astar

```{r}
# We're going to check a grid of all the parameter combinations here
rescue_grid <- cbind(expand.grid("Xmin"=seq(0, 3.5e-7, 5e-8), "kCO2min"=seq(10, 45, 5)),
      expand.grid("Xmax"=seq(5e-8, 4e-7, 5e-8), "kCO2max"=seq(15, 50, 5)))

rescue_grid$rescue_fraction <- rep(NA, nrow(rescue_grid))

for (i in 1:nrow(rescue_grid)) {
      rescue_grid[i, "rescue_fraction"] <- sum(with(rescue_astar,
            X >= rescue_grid[i, "Xmin"] & X < rescue_grid[i, "Xmax"] &
            kCO2 >= rescue_grid[i, "kCO2min"] & kCO2 < rescue_grid[i, "kCO2max"] &
            rescue==TRUE)) / sum(with(rescue_astar,
                  X >= rescue_grid[i, "Xmin"] & X < rescue_grid[i, "Xmax"] &
                  kCO2 >= rescue_grid[i, "kCO2min"] & kCO2 < rescue_grid[i, "kCO2max"]))
}

print(rescue_grid[rescue_grid$rescue_fraction == max(rescue_grid$rescue_fraction),])
```
