---
title: "How long does competitive exclusion of a symbiont take?"
author: "Alexandra Brown and Ross Cunning"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
      html_document:
            code_folding: hide
---

```{r set-options}
# Set kintr options
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, fig.width=8, fig.height=8, results='hold')

# Load packages
library("coRal")
library("foreach")
library("parallel")
library("doParallel")
library("MASS")
library("knitr")

# Plot size for running this in-line
options(repr.plot.res=240)

# Load functions
source("synth.R") # synthesizing unit (used in run_coral_competitive exclusion)
source("cn_limitation.R") # calculates carbon/nitrogen limitation of host and symbiont growth SUs
source("run_coral_competitive_exclusion.R") # run_coral that stops when symbiont 2 has declined to a certain fraction of symbiont 1
source("plotting_functions.R") # some custom plotting functions

# Define colors
colSen <- "#648FFF"
colTol <- "#FFB000"
colNS <- "#000000"
colEither <- "#00FABE"
colRescue <- "#DC267F"

# Define plotting symbols
pchSen <- 1
pchTol <- 19
pchNS <- 0
pchEither <- 3
pchRescue <- 15
```

# Abstract

We want to know:

1. When sensitive and tolerant symbionts are both present in the host, which is superior competitor?
2. How long the host can sustain the inferior competitor at appreciable levels?

We found:

1. Light is the major factor that affects the outcome of symbiont competition. High light favors tolerant symbionts.
2. Food and nitrogen determine host survival at high light but have little effect on which symbiont is the superior competitor.
3. The inferior competitor is lost more slowly when light is intermediate.
4. The amount of symbiont present affects the rate of its competitive exclusion (i.e. log(tolerant/sensitive) vs time is not linear).


# Simulate bleached hosts

```{r set-pars, cache=TRUE}
#### Set parameters ####

# Parameters for determining outcome of symbiont competition. Initialize the symbionts as a
# 50-50 mix. Here sensitive symbiont is symbiont 1; tolerant is symbiont 2
pars_competition <- def_pars(nsym=2)
pars_competition$jCPm[2] <- 1.0
pars_competition$kROS[2] <- 250
pars_competition$jSGm[2] <- 0.15
pars_competition$initS[1:2] <- c(0.5, 0.5)


# To determine how quickly the tolerant symbiont is lost, we set
# the sensitive symbiont to symbiont 1 and the tolerant to symbiont 2 and
# initialize the tolerant symbiont at 99% of the total symbionts
pars_tol_exclusion <- def_pars(nsym=2)
pars_tol_exclusion$jCPm[2] <- 1.0
pars_tol_exclusion$kROS[2] <- 250
pars_tol_exclusion$jSGm[2] <- 0.15
pars_tol_exclusion$initS[1:2] <- c(0.01, 0.99)

# To determine how quickly the sensitive symbiont is lost, we set
# the tolerant symbiont to symbiont 1 and initialize the sensitive symbiont
# at 99% of the total symbionts
pars_sen_exclusion <- def_pars(nsym=2)
pars_sen_exclusion$jCPm[1] <- 1.0
pars_sen_exclusion$kROS[1] <- 250
pars_sen_exclusion$jSGm[1] <- 0.15
pars_sen_exclusion$initS[1:2] <- c(0.01, 0.99)


# Parameters for determining what happens to hosts with a single symbiont species.
# Sensitive symb. parameters
pars_sen <- def_pars(nsym=1)
pars_sen$initS <- 1

# Tolerant symb. parameters
pars_tol <- def_pars(nsym=1)
pars_tol$jCPm <- 1.0
pars_tol$kROS <- 250
pars_tol$jSGm <- 0.15
pars_tol$initS <- 1


# Randomly draw the environmental parameters
env_params <- data.frame("L"=runif(10000, 5, 60), # Light, choose values between 5 and 60 mol photons/m^2/d
                            "N"=runif(10000, 1e-8, 1e-5), # DIN, choose values between 1e-8 and 1e-5 mol/L
                            "X" = runif(10000, 0, 4e-7)) # Food, choose values between 0 and 4e-7 mol/L

# Parameters for symbiont competitive exclusion simulations
threshold <- 0.01/0.99 # Calculate how long it takes for the symbiont to decline to 1% of the total symbionts
max_time <- 365*50 # Give up if threshold has not been reached after 50 years
dt <- 0.1 # Simulate taking time steps of 0.1 day
```


```{r run-competition-sims, cache=TRUE, dependson=c("set-pars")}
#### Determine the outcome of symbiont competition under various environmental conditions ####

# Run simulations for 10 years
time<-seq(0, 10*365, 0.1)

# Set up to run simulations in parallel
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)


# results will temporarily hold the summary statistics from the simulations
results <- foreach(i=1:nrow(env_params), .combine='rbind', .packages='dplyr') %dopar% {

  # Set up the environmental conditions
  env <- coRal::init_env(time=time, L=c(env_params[i, "L"], env_params[i, "L"], 0),
    N=c(env_params[i, "N"], env_params[i, "N"], 0), X=c(env_params[i, "X"], env_params[i, "X"], 0))

  # Run the simulation
  run <- coRal::run_coral(time=time, env=env, pars=pars_competition)

  # Calculate C-N limitation
  cnlim <- cn_limitation(run, pars_competition)

  # Possible measures of host healthy and functional symbiosis:
  #host growth, lack of carbon limitation
  posGrH <- (run$dH.Hdt[length(time)] > 0) # Is host growth positive?
  noClimH <- (cnlim$H[length(time)] >= 0) # Is host NOT carbon-limited?
  noClimS.1 <- (cnlim$S.1[length(time)] >= 0) # Is the sensitive symb. NOT carbon-limited?
  noClimS.2 <- (cnlim$S.2[length(time)] >= 0) # Is the tolerant symb. NOT carbon-limited?
  noClimAll <- noClimH & noClimS.1 & noClimS.2 # Are parties NOT carbon-limited?

  # Which symbiont is the superior competitor?
  logTS <- log(run$S.2[length(time)]) - log(run$S.1[length(time)]) # log sensitive:tolerant ratio
  grS.1 <- run$dS.Sdt.1[length(time)] # Sensitive symb. per capita growth rate
  grS.2 <- run$dS.Sdt.2[length(time)] # Tolerant symb. per capita growth rate

  if(posGrH & noClimAll) {
      if(logTS > 0) {
        sup_competitor <- "Tolerant" # There are more tolerant than sensitive symbionts
      } else if(logTS < 0) {
        sup_competitor <- "Sensitive" # More sensitive than tolerant symbionts
      } else if(logTS == 0) {
        sup_competitor <- "Equal-competitors" # Equal amounts of symbionts
      } else {
        sup_competitor <- NA # if logTS is not a number, something's gone wrong
      }
  } else {
    sup_competitor <- "No-survival" # The host is dead so symbiont competition doesn't matter
  }

  # Return the environmental parameters, survival and competition information
  list("L"=env_params[i, "L"], "N"=env_params[i, "N"], "X"=env_params[i, "X"],
    "posGrH"=posGrH, "noClimAll"=noClimAll, "logTS"=logTS,
    "grS.1"=grS.1, "grS.2"=grS.2, "sup_competitor"=sup_competitor)
}

# Stop the cluster
stopCluster(cl)

# Store results in dataframe, set column types
sim_competition <- data.frame(results, row.names=NULL)
sim_competition <- transform(sim_competition, L=as.numeric(L), N=as.numeric(N), X=as.numeric(X),
  posGrH=as.logical(posGrH), noClimAll=as.logical(noClimAll), logTS=as.numeric(logTS),
  grS.1=as.numeric(grS.1), grS.2=as.numeric(grS.2),
  sup_competitor=factor(sup_competitor, levels=c("Sensitive", "Tolerant", "No-survival", "Equal-competitors")))
```


```{r run-single-symb-sims, cache=TRUE, dependson=c("set-pars")}

#### Determine where hosts can survive with a single symbiont  ####

# Run simulations for 2 years
time<-seq(0, 2*365, 0.1)

# Set up to run simulations in parallel
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)


# results will temporarily hold the summary statistics from the simulations
results <- foreach(i=1:nrow(env_params), .combine='rbind', .packages='dplyr') %dopar% {

  # Set up the environmental conditions
  env <- coRal::init_env(time=time, L=c(env_params[i, "L"], env_params[i, "L"], 0),
    N=c(env_params[i, "N"], env_params[i, "N"], 0), X=c(env_params[i, "X"], env_params[i, "X"], 0))

  # Run the simulation
  run_sen <- coRal::run_coral(time=time, env=env, pars=pars_sen)
  run_tol <- coRal::run_coral(time=time, env=env, pars=pars_tol)

  # Calculate C-N limitation
  cnlim_sen <- cn_limitation(run_sen, pars_sen)
  cnlim_tol <- cn_limitation(run_sen, pars_tol)

  # Possible measures of host healthy and functional symbiosis:
  # host growth, lack of carbon limitation
  posGrH_sen <- (run_sen$dH.Hdt[length(time)] > 0) # Is host growth positive?
  posGrH_tol <- (run_tol$dH.Hdt[length(time)] > 0)
  noClimH_sen <- (cnlim_sen$H[length(time)] >= 0) # Is host NOT carbon-limited?
  noClimH_tol <- (cnlim_tol$H[length(time)] >= 0)
  noClimS_sen <- (cnlim_sen$S[length(time)] >= 0) # Is the symbiont NOT carbon-limited?
  noClimS_tol <- (cnlim_tol$S[length(time)] >= 0)
  noClimAll_sen <- noClimH_sen & noClimS_sen  # Are both parties NOT carbon-limited?
  noClimAll_tol <- noClimH_tol & noClimS_tol


  # Which symbiont(s) can the host survive with?
    if(posGrH_sen & noClimAll_sen) {
      if(posGrH_tol & noClimAll_tol) {
        survival_1symb <- "Either" # Host can survive with either sensitive or tolerant symbiont
      } else {
        survival_1symb <- "Sensitive" # Host can survive with only the sensitive symbiont
      }
    } else if(posGrH_tol & noClimAll_tol) {
      survival_1symb <- "Tolerant" # Host can survive with only the tolerant symbiont
    } else {
      survival_1symb <- "No-survival" # Host cannot survive with either symbiont
    }


  # Return the environmental parameters, survival and competition information
  list("L"=env_params[i, "L"], "N"=env_params[i, "N"], "X"=env_params[i, "X"],
    "posGrH_sen"=posGrH_sen, "posGrH_tol"=posGrH_tol, "noClimAll_sen"=noClimAll_sen,
    "noClimAll_tol"=noClimAll_tol, "survival_1symb"=survival_1symb)
}

# Stop the cluster
stopCluster(cl)

# Store results in dataframe, set column types
sim_1symb <- data.frame(results, row.names=NULL)
sim_1symb <- transform(sim_1symb, L=as.numeric(L), N=as.numeric(N), X=as.numeric(X),
  posGrH_sen=as.logical(posGrH_sen), posGrH_tol=as.logical(posGrH_sen),
  noClimAll_sen=as.logical(noClimAll_sen), noClimAll_tol=as.logical(noClimAll_tol),
  survival_1symb=factor(survival_1symb, levels=c("Sensitive", "Tolerant", "Either", "No-survival")))
```


```{r run-tolerant-exclusion-sims, cache=TRUE, dependson=c("set-pars", "run-competition-sims")}
#### Simulate the competitive exclusion of the tolerant symbiont ####

# Get the environments where the tolerant symbiont should be lost over time
env_tol_exclusion <- sim_competition[sim_competition$sup_competitor == "Sensitive", c("L", "N", "X")]

# Set up to run simulations in parallel
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

# Results will temporarily hold the summary statistics from the simulations
results <- foreach(i=1:nrow(env_tol_exclusion), .combine='rbind', .packages='dplyr') %dopar% {

  # Set up the environmental conditions
  env <- list(L=env_tol_exclusion[i, "L"], N=env_tol_exclusion[i, "N"], X=env_tol_exclusion[i, "X"])

  # Run the simulation
  run <- run_coral_comp_exclusion(env=env, pars=pars_tol_exclusion, max_time=max_time, dt=dt, threshold=threshold)

  # Was the threshold tolerant:sensitive ratio reached?
  reachedThreshold <- run$reachedThreshold

  # If so, when was the threshold reached?
  if(reachedThreshold) {
    exclusionTime <- run$fluxes$time[length(run$fluxes$time)]
  } else {
    exclusionTime <- NA
  }
  print("Got here")
  # Check that the host is alive
  cnlim <- cn_limitation(run$fluxes, pars_tol_exclusion) # Calculate carbon/nitrogen limitation
  posGrH <- (run$fluxes$dH.Hdt[length(run$fluxes$dH.Hdt)] > 0) # Is the host growing?
  noClimH <- (cnlim$H[length(time)] >= 0) # Is host NOT carbon-limited?
  noClimS.1 <- (cnlim$S.1[length(time)] >= 0) # Is the sensitive symb. NOT carbon-limited?
  noClimS.2 <- (cnlim$S.2[length(time)] >= 0) # Is the tolerant symb. NOT carbon-limited?
  noClimAll <- noClimH & noClimS.1 & noClimS.2 # Are parties NOT carbon-limited?

  # Check that host was alive at 100 days post-initialization
  time <- seq(0, 100, 0.1)
  env <- coRal::init_env(time, L=c(env_tol_exclusion[i, "L"], env_tol_exclusion[i, "L"], 0),
    N=c(env_tol_exclusion[i, "N"], env_tol_exclusion[i, "N"], 0), X=c(env_tol_exclusion[i, "X"], env_tol_exclusion[i, "X"], 0))

  run_survival <- coRal::run_coral(time=time, env=env, pars=pars_tol_exclusion)

  cnlim100d <- cn_limitation(run_survival, pars_tol_exclusion) # Calculate carbon/nitrogen limitation
  posGrH100d <- (run_survival$dH.Hdt[length(time)] > 0) # Is the host growing?
  noClimH100d <- (cnlim100d$H[length(time)] >= 0) # Is host NOT carbon-limited?
  noClimS100d.1 <- (cnlim100d$S.1[length(time)] >= 0) # Is the sensitive symb. NOT carbon-limited?
  noClimS100d.2 <- (cnlim100d$S.2[length(time)] >= 0) # Is the tolerant symb. NOT carbon-limited?
  noClimAll100d <- noClimH100d & noClimS100d.1 & noClimS100d.2 # Are parties NOT carbon-limited?

  # Return environmental parameters, whether the threshold was reached, and, if so, when
  list("L"=env_tol_exclusion[i, "L"], "N"=env_tol_exclusion[i, "N"], "X"=env_tol_exclusion[i, "X"],
    "reachedThreshold"=reachedThreshold, "exclusionTime"=exclusionTime, "posGrH"=posGrH,
    "noClimAll"=noClimAll, "posGrH100d"=posGrH100d, "noClimAll100d"=noClimAll100d)
}

# Stop the cluster
stopCluster(cl)

# Store results in dataframe, set column types
sim_tol_exclusion <- data.frame(results, row.names=NULL)
sim_tol_exclusion <- transform(sim_tol_exclusion, L=as.numeric(L), N=as.numeric(N), X=as.numeric(X),
  reachedThreshold=as.logical(reachedThreshold), exclusionTime=as.numeric(exclusionTime),
  posGrH=as.logical(posGrH), noClimAll=as.logical(noClimAll),
  posGrH100d=as.logical(posGrH100d), noClimAll100d=as.logical(noClimAll100d))

```



```{r run-sensitive-exclusion-sims, cache=TRUE, dependson=c("set-pars", "run-competition-sims")}
#### Simulate the competitive exclusion of the sensitive symbiont ####

# Get the environments where the sensitive symbiont should be lost over time
env_sen_exclusion <- sim_competition[sim_competition$sup_competitor == "Tolerant", c("L", "N", "X")]

# Set up to run simulations in parallel
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

# Results will temporarily hold the summary statistics from the simulations
results <- foreach(i=1:nrow(env_sen_exclusion), .combine='rbind', .packages='dplyr') %dopar% {

  # Set up the environmental conditions
  env <- list(L=env_sen_exclusion[i, "L"], N=env_sen_exclusion[i, "N"], X=env_sen_exclusion[i, "X"])

  # Run the simulation
  run <- run_coral_comp_exclusion(env=env, pars=pars_sen_exclusion, max_time=max_time, dt=dt, threshold=threshold)

  # Was the threshold tolerant:sensitive ratio reached?
  reachedThreshold <- run$reachedThreshold

  # If so, when was the threshold reached?
  if(reachedThreshold) {
    exclusionTime <- run$fluxes$time[length(run$fluxes$time)]
  } else {
    exclusionTime <- NA
  }

  # Check that the host is alive
  cnlim <- cn_limitation(run$fluxes, pars_sen_exclusion) # Calculate carbon/nitrogen limitation
  posGrH <- (run$fluxes$dH.Hdt[length(run$fluxes$dH.Hdt)] > 0) # Is the host growing?
  noClimH <- (cnlim$H[length(time)] >= 0) # Is host NOT carbon-limited?
  noClimS.1 <- (cnlim$S.1[length(time)] >= 0) # Is the sensitive symb. NOT carbon-limited?
  noClimS.2 <- (cnlim$S.2[length(time)] >= 0) # Is the tolerant symb. NOT carbon-limited?
  noClimAll <- noClimH & noClimS.1 & noClimS.2 # Are parties NOT carbon-limited?

  # Check that host was alive at 100 days post-initialization
  time <- seq(0, 100, 0.1)
  env <- coRal::init_env(time, L=c(env_sen_exclusion[i, "L"], env_sen_exclusion[i, "L"], 0),
    N=c(env_sen_exclusion[i, "N"], env_sen_exclusion[i, "N"], 0), X=c(env_sen_exclusion[i, "X"], env_sen_exclusion[i, "X"], 0))

  run_survival <- coRal::run_coral(time=time, env=env, pars=pars_sen_exclusion)

  cnlim100d <- cn_limitation(run_survival, pars_sen_exclusion) # Calculate carbon/nitrogen limitation
  posGrH100d <- (run_survival$dH.Hdt[length(time)] > 0) # Is the host growing?
  noClimH100d <- (cnlim100d$H[length(time)] >= 0) # Is host NOT carbon-limited?
  noClimS100d.1 <- (cnlim100d$S.1[length(time)] >= 0) # Is the sensitive symb. NOT carbon-limited?
  noClimS100d.2 <- (cnlim100d$S.2[length(time)] >= 0) # Is the tolerant symb. NOT carbon-limited?
  noClimAll100d <- noClimH100d & noClimS100d.1 & noClimS100d.2 # Are parties NOT carbon-limited?

  # Return environmental parameters, whether the threshold was reached, and, if so, when
  list("L"=env_sen_exclusion[i, "L"], "N"=env_sen_exclusion[i, "N"], "X"=env_sen_exclusion[i, "X"],
    "reachedThreshold"=reachedThreshold, "exclusionTime"=exclusionTime, "posGrH"=posGrH,
    "noClimAll"=noClimAll, "posGrH100d"=posGrH100d, "noClimAll100d"=noClimAll100d)
}

# Stop the cluster
stopCluster(cl)

# Store results in dataframe, set column types
sim_sen_exclusion <- data.frame(results, row.names=NULL)
sim_sen_exclusion <- transform(sim_sen_exclusion, L=as.numeric(L), N=as.numeric(N), X=as.numeric(X),
  reachedThreshold=as.logical(reachedThreshold), exclusionTime=as.numeric(exclusionTime),
  posGrH=as.logical(posGrH), noClimAll=as.logical(noClimAll),
  posGrH100d=as.logical(posGrH100d), noClimAll100d=as.logical(noClimAll100d))

```

# Where is each symbiont the superior competitor?

```{r plot-symb-competition, cache=TRUE, dependson=c("run-competition-sims"), fig.width=10, fig.height=5}
#### Linear discriminant analysis ####

# Center and scale the environmental variables
datalda <- sim_competition[, c("sup_competitor", "L", "N", "X")]
datalda$L <- (datalda$L - mean(datalda$L))/sd(datalda$L)
datalda$N <- (datalda$N - mean(datalda$N))/sd(datalda$N)
datalda$X <- (datalda$X - mean(datalda$X))/sd(datalda$X)

# Run the linear discriminant analysis
outlda <- lda(sup_competitor ~ L + N + X, datalda)

# Plot the data on the linear discriminant axes
#pdf("sup_competitor.pdf", 10, 5)
layout(matrix(c(1, 1, 2, 3, 1, 1, 4, 5), nrow=2, byrow=TRUE), respect=TRUE)

plot(predict(outlda)$x[,1], predict(outlda)$x[,2],
  col=c(transparent(colSen, 0.25), transparent(colTol, 0.25), transparent(colNS, 0.25))[datalda$sup_competitor],
	pch=c(pchSen, pchTol, pchNS)[datalda$sup_competitor],
  xlab="LD 1", ylab="LD 2", main="(a) Linear discriminant analysis")

# Add arrows representing the environmental variables in LD space
arrows(x0=0, y0=0, x1=1.5*outlda$scaling[1,1], y1=1.5*outlda$scaling[1,2], length=0.1, col="white", lwd=5)
arrows(x0=0, y0=0, x1=1.5*outlda$scaling[1,1], y1=1.5*outlda$scaling[1,2], length=0.1, col="black", lwd=2)
rect(xleft=1.25*outlda$scaling[1,1] - strwidth("Light")/2 - 0.1, ybottom=1.25*outlda$scaling[1,2] - 0.5*strheight("Light") + 0.15,
  xright=1.25*outlda$scaling[1,1] + strwidth("Light")/2 + 0.1, ytop=1.25*outlda$scaling[1,2] + 0.5*strheight("Light") + 0.35,
  col="white", border=NA)
text(x=1.25*outlda$scaling[1,1], y=1.25*outlda$scaling[1,2] + 0.25, labels="Light", col="black")

arrows(x0=0, y0=0, x1=1.5*outlda$scaling[2,1], y1=1.5*outlda$scaling[2,2], length=0.1, col="white", lwd=5)
arrows(x0=0, y0=0, x1=1.5*outlda$scaling[2,1], y1=1.5*outlda$scaling[2,2], length=0.1, col="black", lwd=2)
rect(xleft=1.25*outlda$scaling[2,1] - strwidth("Nitrogen") - 0.35, ybottom=1.25*outlda$scaling[2,2] - 0.5*strheight("Nitrogen") - 0.1,
  xright=1.25*outlda$scaling[2,1] - 0.15, ytop=1.25*outlda$scaling[2,2] + 0.5*strheight("Nitrogen") + 0.1,
  col="white", border=NA)
text(x=1.25*outlda$scaling[2,1] - 0.25, y=1.25*outlda$scaling[2,2], adj=1, labels="Nitrogen", col="black")

arrows(x0=0, y0=0, x1=1.5*outlda$scaling[3,1], y1=1.5*outlda$scaling[3,2], length=0.1, col="white", lwd=5)
arrows(x0=0, y0=0, x1=1.5*outlda$scaling[3,1], y1=1.5*outlda$scaling[3,2], length=0.1, col="black", lwd=2)
rect(xleft=1.25*outlda$scaling[3,1] - strwidth("Food") - 0.35, ybottom=1.25*outlda$scaling[3,2] - 0.5*strheight("Food") - 0.1,
  xright=1.25*outlda$scaling[3,1] - 0.15, ytop=1.25*outlda$scaling[3,2] + 0.5*strheight("Food") + 0.1,
  col="white", border=NA)
text(x=1.25*outlda$scaling[3,1] - 0.25, y=1.25*outlda$scaling[3,2], adj=1, labels="Food", col="black")

#### Plot competition outcome vs each environmental variable ####

stackedHist(data=list(sim_competition$L[(sim_competition$sup_competitor == "Sensitive")],
  sim_competition$L[(sim_competition$sup_competitor == "Tolerant")],
  sim_competition$L[(sim_competition$sup_competitor == "No-survival")]),
  breaks=seq(5, 60, 2.5), xlim=c(5, 60), colors=c(colSen, colTol, colNS),
  xlab="Light (mol photons/m^2/day)", ylab="% Simulations", main="(b) Light")


stackedHist(data=list(sim_competition$N[(sim_competition$sup_competitor == "Sensitive")],
  sim_competition$N[(sim_competition$sup_competitor == "Tolerant")],
  sim_competition$N[(sim_competition$sup_competitor == "No-survival")]),
  colors=c(colSen, colTol, colNS),
  xlab="Nitrogen (mol/L)", ylab="% Simulations", main="(c) Nitrogen")

stackedHist(data=list(sim_competition$X[(sim_competition$sup_competitor == "Sensitive")],
  sim_competition$X[(sim_competition$sup_competitor == "Tolerant")],
  sim_competition$X[(sim_competition$sup_competitor == "No-survival")]),
  colors=c(colSen, colTol, colNS),
  xlab="Food (mol/L)", ylab="% Simulations", main="(d) Food")

# Legend
plot.new()
legend("center", c("Sensitive symb.", "Tolerant symb.", "No survival"),
	col=c(colSen, colTol, colNS), pch=c(pchSen, pchTol, pchNS),
	title="Legend: Superior competitor", cex=1.3, pt.cex=1.5)
#dev.off()

# Print the results of the linear discriminant analysis
outlda
```


# How long does it take for the inferior competitor to be competitively excluded (i.e. to be <= 1% of the total symbionts)?

```{r plot-exclusion-time-distribution, cache=TRUE, dependson=c("run-tolerant-exclusion-sims", "run-sensitive-exclusion-sims"), fig.width=12, fig.height=6}

# Use the histogram function to sort the times to competitive exclusion into bins
breaks <- c(seq(0, 365, length.out=7), 1.5*365, 2*365, 5*365, seq(25*365, 100*365, 25*365))

hist_tol_exclusion <- hist(sim_tol_exclusion$exclusionTime[sim_tol_exclusion$reachedThreshold],
  breaks=breaks, plot=FALSE)

hist_sen_exclusion <- hist(sim_sen_exclusion$exclusionTime[sim_sen_exclusion$reachedThreshold],
  breaks=breaks, plot=FALSE)

# Convert bin heights to % of simulations
hist_tol_exclusion$density <- hist_tol_exclusion$counts / nrow(sim_tol_exclusion) * 100
hist_sen_exclusion$density <- hist_sen_exclusion$counts / nrow(sim_sen_exclusion) * 100

# Put the bin heights together in a matrix
exclusion_time_mat <- matrix(c(hist_tol_exclusion$density, hist_sen_exclusion$density), byrow=TRUE, nrow=2)

# Add a column to the matrix for exclusion times > 2 years
exclusion_time_mat <- cbind(exclusion_time_mat, c(NA, NA))
exclusion_time_mat[1, ncol(exclusion_time_mat)] <- sum(!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll) / nrow(sim_tol_exclusion) * 100
exclusion_time_mat[2, ncol(exclusion_time_mat)] <- sum(!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll) / nrow(sim_sen_exclusion) * 100

# Add a column for death of host
exclusion_time_mat <- cbind(c(NA, NA), exclusion_time_mat)
exclusion_time_mat[1, 1] <- sum(!(sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll)) / nrow(sim_tol_exclusion) * 100
exclusion_time_mat[2, 1] <- sum(!(sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll)) / nrow(sim_sen_exclusion) * 100


# Barplot
par(cex.axis=0.75)
barplot(exclusion_time_mat,
	names=c("Host dies", paste0(seq(0, 10, 2), "-", seq(2, 12, 2), " mo"), "1-1.5 yr", "1.5-2 yr", "2-5 yr", "5-25 yr", "25-50 yr", "50-100 yr", ">100 yr"),
	xlab="Time till inferior competitor declines to 1% of total symbionts", ylab="% of simulations",
  main="Time it takes inferior competitor to be competitively excluded",
	beside=TRUE, col=c(colTol, colSen))

legend("topleft", c("Comp. exclusion of tol. symb.", "Comp. exclusion of sen. symb"), pch=22,
  pt.bg=c(colTol, colSen), col="black")
```


# How do environmental variables affect the time to competitive exclusion?

```{r plot-environment-vs-exclusion, cache=TRUE, dependson=c("run-tolerant-exclusion-sims", "run-sensitive-exclusion-sims")}
par(mfrow=c(2, 2))

## Light

plot(sim_tol_exclusion$L[sim_tol_exclusion$reachedThreshold & sim_tol_exclusion$posGrH],
	sim_tol_exclusion$exclusionTime[sim_tol_exclusion$reachedThreshold & sim_tol_exclusion$posGrH]/365,
	xlim=c(5, 60), ylim=c(1/365, 100+1), xlab="Light (mol photons/m^2/day)",
	ylab="Time to competitive exclusion (years)", col=colTol, pch=pchTol,
	main="(a) Light")

points(sim_sen_exclusion$L[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH],
	sim_sen_exclusion$exclusionTime[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH]/365,
	col=colSen, pch=pchSen)

points(sim_tol_exclusion$L[!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH],
	rep(11, sum(!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH)),
	col=colTol, pch=17)

points(sim_sen_exclusion$L[!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH],
	rep(11, sum(!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH)),
	col=colSen, pch=2)

# dtol <- density(sim_tol_exclusion$L[!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH])
# dsen <- density(sim_sen_exclusion$L[!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH])
# plot(dtol, xlab="", ylab="", xlim=c(5, 60), main="", col=colTol, lwd=2, type="l")
# lines(dsen, col=colSen)


## Nitrogen

plot(sim_tol_exclusion$N[sim_tol_exclusion$reachedThreshold & sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll],
	sim_tol_exclusion$exclusionTime[sim_tol_exclusion$reachedThreshold & sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll],
	xlim=c(1e-8, 1e-5), ylim=c(1/365, 100+1), xlab="Nitrogen (mol/L)",
	ylab="Time to competitive exclusion (years)", col=colTol, pch=pchTol,
	main="(b) Nitrogen")

points(sim_sen_exclusion$N[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll],
	sim_sen_exclusion$exclusionTime[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll],
	col=colSen, pch=pchSen)

points(sim_tol_exclusion$N[!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll],
	rep(10*365+20, sum(!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll)),
	col=colTol, pch=17)

points(sim_sen_exclusion$N[!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll],
	rep(10*365+20, sum(!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll)),
	col=colSen, pch=2)


## Food

plot(sim_tol_exclusion$X[sim_tol_exclusion$reachedThreshold & sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll],
	sim_tol_exclusion$exclusionTime[sim_tol_exclusion$reachedThreshold & sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll],
	xlim=c(0, 4e-7), ylim=c(1/365, 100+1), xlab="Food (mol/L)",
	ylab="Time to competitive exclusion (years)", col=colTol, pch=pchTol,
	main="(c) Food")

points(sim_sen_exclusion$X[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll],
	sim_sen_exclusion$exclusionTime[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll],
	col=colSen, pch=pchSen)

points(sim_tol_exclusion$X[!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll],
	rep(10*365+20, sum(!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll)),
	col=colTol, pch=17)

points(sim_sen_exclusion$X[!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll],
	rep(10*365+20, sum(!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll)),
	col=colSen, pch=2)


## Legend

```


```{r}

par(mfrow=c(2,2))
myhist <- hist(sim_tol_exclusion$L, xlab="Light (mol photons/m^2/day)", ylab="# sims")
hist(sim_tol_exclusion$L[!(sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll)], add=TRUE, breaks=myhist$breaks, col=rgb(0, 0, 1, 0.25))

myhist <- hist(sim_tol_exclusion$N, xlab="Nitrogen (mol/L)", ylab="# sims")
hist(sim_tol_exclusion$N[!(sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll)], add=TRUE, breaks=myhist$breaks, col=rgb(0, 0, 1, 0.25))

myhist <- hist(sim_tol_exclusion$X, xlab="Food (mol/L)", ylab="# sims")
hist(sim_tol_exclusion$X[!(sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll)], add=TRUE, breaks=myhist$breaks, col=rgb(0, 0, 1, 0.25))

plot.new()
legend("top", c("All sims w/ sen. sup. comp.", "Host dies"),
	pch=22, col="black", pt.bg=c("white", rgb(0, 0, 1, 0.25)))



par(mfrow=c(2,2))
myhist <- hist(sim_sen_exclusion$L, xlab="Light (mol photons/m^2/day)", ylab="# sims")
hist(sim_sen_exclusion$L[!(sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll)], add=TRUE, breaks=myhist$breaks, col=rgb(0, 0, 1, 0.25))

myhist <- hist(sim_sen_exclusion$N, xlab="Nitrogen (mol/L)", ylab="# sims")
hist(sim_sen_exclusion$N[!(sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll)], add=TRUE, breaks=myhist$breaks, col=rgb(0, 0, 1, 0.25))

myhist <- hist(sim_sen_exclusion$X, xlab="Food (mol/L)", ylab="# sims")
hist(sim_sen_exclusion$X[!(sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll)], add=TRUE, breaks=myhist$breaks, col=rgb(0, 0, 1, 0.25))

plot.new()
legend("top", c("All sims tol. sup. comp.", "Host dies"),
	pch=22, col="black", pt.bg=c("white", rgb(0, 0, 1, 0.25)))
```

# What do the dynamics of competitive exclusion look like?

```{r plot-exclusion-dynamics, cache=TRUE, dependson=c("set-pars", "run-tolerant-exclusion-sims", "run-sensitive-exclusion-sims")}
time <- seq(0, 2*365)

par(mfrow=c(4,3))
for(i in 1:4) {
  Li <- sim_tol_exclusion[i, "L"]
  Ni <- sim_tol_exclusion[i, "N"]
  Xi <- sim_tol_exclusion[i, "X"]

  env <- init_env(time=time, L=c(Li, Li, 0), N=c(Ni, Ni, 0), X=c(Xi, Xi, 0))

  run <- coRal::run_coral(time=time, env=env, pars=pars_tol_exclusion)
  run2 <- coRal::run_coral(time=time, env=env, pars=pars_competition)

  minSH <- min(run$S.1/run$H, run$S.2/run$H)
  maxSH <- max(run$S.1/run$H, run$S.2/run$H)

  plot(time, run$S.1/run$H, type="l", col=colSen, xlab="time (days)", ylab="S/H ratio",
    main=paste("Sim", i), ylim=c(minSH, maxSH), log="y")
  lines(time, run$S.2/run$H, col=colTol)

  minSH <- min(run2$S.1/run2$H, run2$S.2/run2$H)
  maxSH <- max(run2$S.1/run2$H, run2$S.2/run2$H)

  plot(time, run2$S.1/run2$H, type="l", col=colSen, xlab="time (days)", ylab="S/H ratio",
    main=paste("Sim", i), ylim=c(minSH, maxSH), log="y")
  lines(time, run2$S.2/run2$H, col=colTol)

  minGr <- min(c(run$dH.Hdt[-1], run2$dH.Hdt[-1]))
  maxGr <- max(c(run$dH.Hdt[-1], run2$dH.Hdt[-1]))

  plot(time[-1], run$dH.Hdt[-1], col="gray", type="l", lwd=2, xlab="time (days)",
  ylab="Host growth rate", main=paste("Sim", i), ylim=c(minGr, maxGr))

  lines(time[-1], run2$dH.Hdt[-1], col="black")
}
```

```{r}
par(mfrow=c(2,2))

i <- 2

Li <- sim_tol_exclusion[i, "L"]
Ni <- sim_tol_exclusion[i, "N"]
Xi <- sim_tol_exclusion[i, "X"]

env <- init_env(time=time, L=c(Li, Li, 0), N=c(Ni, Ni, 0), X=c(Xi, Xi, 0))

run <- coRal::run_coral(time=time, env=env, pars=pars_tol_exclusion)
run2 <- coRal::run_coral(time=time, env=env, pars=pars_competition)

minSH <- min(run$S.1/run$H, run$S.2/run$H)
maxSH <- max(run$S.1/run$H, run$S.2/run$H)

plot(time, run$S.1/run$H, type="l", col=colSen, xlab="time (days)", ylab="S/H ratio",
  main="Initialized with 1 C-mol host\n0.5 C-mol S. symb, 0.5 C-mol T. symb",
  ylim=c(minSH, maxSH), log="y")
lines(time, run$S.2/run$H, col=colTol)

legend("topright", c("Sensitive (S) symb.", "Tolerant (T) symb."),
  lwd=c(1, 1), col=c(colSen, colTol))

minSH <- min(run2$S.1/run2$H, run2$S.2/run2$H)
maxSH <- max(run2$S.1/run2$H, run2$S.2/run2$H)

plot(time, run2$S.1/run2$H, type="l", col=colSen, xlab="time (days)", ylab="S/H ratio",
  main="Initialized with 1 C-mol host\n0.01 C-mol S. symb, 0.99 C-mol T. symb",
  ylim=c(minSH, maxSH), log="y")
lines(time, run2$S.2/run2$H, col=colTol)

legend("topright", c("Sensitive (S) symb.", "Tolerant (T) symb."),
  lwd=c(1, 1), col=c(colSen, colTol))

minGr <- min(c(run$dH.Hdt[-1], run2$dH.Hdt[-1]))
maxGr <- max(c(run$dH.Hdt[-1], run2$dH.Hdt[-1]))

plot(time[-1], run$dH.Hdt[-1], col="gray", type="l", lwd=2, xlab="time (days)",
ylab="Host per capita growth rate", main="Host growth rate\n(both initial conditions)", ylim=c(minGr, maxGr))

lines(time[-1], run2$dH.Hdt[-1], col="black")

legend("topright", c("0.5 C-mol S, 0.5 C-mol T", "0.01 C-mol S, 0.99 C-mol T"),
  lwd=c(2, 1), col=c("gray", "black"))

print(paste0("Light = ", Li, " mol photons/m^2/day, Nitrogen = ", Ni, " mol/L, Food = ", Xi, " mol/L"))
```


```{r}
# How many cases where the sensitive symb. was the superior competitor were in environments where the host could only survive
# with the sensitive symbiont?
sum((sim_competition$sup_competitor == "Sensitive") &
	(sim_1symb$survival_1symb == "Sensitive")) / sum(sim_competition$sup_competitor == "Sensitive")

# How many of those were where the host could survive with either symbiont?
sum((sim_competition$sup_competitor == "Sensitive") &
	(sim_1symb$survival_1symb == "Either")) / sum(sim_competition$sup_competitor == "Sensitive")

# How many were where the host couldn't survive with the sensitive symbiont at all (this would be weird)?
sum((sim_competition$sup_competitor == "Sensitive") & ((sim_1symb$survival_1symb == "Tolerant") |
	(sim_1symb$survival_1symb == "No-survival"))) / sum(sim_competition$sup_competitor == "Sensitive")





# How many cases where the tolerant symb. was the superior competitor were in environments where the host could only survive
# with the tolerant symbiont?
sum((sim_competition$sup_competitor == "Tolerant") &
	(sim_1symb$survival_1symb == "Tolerant")) / sum(sim_competition$sup_competitor == "Tolerant")

# How many of those were where the host could survive with either symbiont?
sum((sim_competition$sup_competitor == "Tolerant") &
	(sim_1symb$survival_1symb == "Either")) / sum(sim_competition$sup_competitor == "Tolerant")

# How many were there where the host couldn't survive with the tolerant symbiont at all (this would be weird)?
sum((sim_competition$sup_competitor == "Tolerant") & ((sim_1symb$survival_1symb == "Sensitive") |
	(sim_1symb$survival_1symb == "No-survival"))) / sum(sim_competition$sup_competitor == "Tolerant")



## These statistics don't neccesarily line up perfectly with being able to survive with 99% of the inferior competitor
# How many cases where sensitive symb. was the superior competitor and the host failed to survive with 99% tolerant were in regions
# where the host couldn't survive with the tolerant symbiont alone? (all but literally 1 case)
sen_1symb <- sim_1symb[sim_competition$sup_competitor == "Sensitive",]
sum((sen_1symb$survival_1symb == "Sensitive") & !(sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll)) / sum(!(sim_tol_exclusion$posGrH & sim_tol_exclusion$noClimAll))

# How many cases where the tolerant was the superior competitor and the host failed to survive with 99% sensitive were in regions
# where the host couldn't survive with the sensitive symbiont alone? (all cases)
tol_1symb <- sim_1symb[sim_competition$sup_competitor == "Tolerant",]
sum((tol_1symb$survival_1symb == "Tolerant") & !(sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll)) / sum(!(sim_sen_exclusion$posGrH & sim_sen_exclusion$noClimAll))



# # Let's look at that one case where the host could survive with either alone but not with 99% tolerant
# pt <- sim_tol_exclusion[!(sim_tol_exclusion$posGrH) & (sen_1symb$survival_1symb != "Sensitive"),]
# time <- seq(0, 3*365, 0.1)
# env <- init_env(time, L=c(pt$L, pt$L, 0), N=c(pt$N, pt$N, 0), X=c(pt$X, pt$X, 0))
# run <- run_coral(time, env, pars_tol_exclusion)
# plot(time, run$S.1/run$H, col=colSen, type="l", ylim=c(0, max(c(run$S.1/run$H, run$S.2/run$H))))
# lines(time, run$S.2/run$H, col=colTol)
# plot(time[-1], run$dH.Hdt[-1], type="l")
# lines(time, rep(0, length(time)), col="pink")
#
# runS <- run_coral(time, env, pars_sen)
# plot(time, runS$S/runS$H, type="l")
# plot(time[-1], runS$dH.Hdt[-1], type="l")
# lines(time, rep(0, length(time)), col="pink")
#
# runT <- run_coral(time, env, pars_tol)
# plot(time, runT$S/runT$H, type="l")
# plot(time[-1], runT$dH.Hdt[-1], type="l")
# lines(time, rep(0, length(time)), col="pink")
```
