---
title: "How long does competitive exclusion of a symbiont take?"
author: "A.L. Brown. F. Pfab, E.C. Baxter, A.R. Detmer, H.V. Moeller, R.M. Nisbet, and R. Cunning"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
      html_document:
            code_folding: hide
---

```{r set-options}
  # Set kintr options
  knitr::opts_chunk$set(echo = TRUE, cache = FALSE, fig.width=8, fig.height=8, results='hold')

  # Load packages
  library("coRal")
  library("foreach")
  library("parallel")
  library("doParallel")
  library("MASS")
  library("knitr")

  # Plot size for running this in-line
  options(repr.plot.res=240)

  # Load functions
  source("R_functions/synth.R") # synthesizing unit (used in run_coral_competitive exclusion)
  source("R_functions/cn_limitation.R") # calculates carbon/nitrogen limitation of host and symbiont growth SUs
  source("R_functions/run_coral_competitive_exclusion.R") # run_coral that stops when symbiont 2 has declined to a certain fraction of symbiont 1
  source("R_functions/plotting_functions.R") # some custom plotting functions

  # Define colors
  colSen <- "#648FFF"
  colTol <- "#FFB000"
  colNS <- "#000000"
  colEither <- "#00FABE"
  colRescue <- "#DC267F"

  # Define plotting symbols
  pchSen <- 1
  pchTol <- 19
  pchNS <- 0
  pchEither <- 3
  pchRescue <- 15
```

# Abstract

  We want to know:

  1. When sensitive and tolerant symbionts are both present in the host, which is superior competitor?
  2. How long the host can sustain the inferior competitor at appreciable levels?

  We found:

  1. Light is the major factor that affects the outcome of symbiont competition. High light favors tolerant symbionts.
  2. At high light, low nitrogen increases hosts' chances of survival/maintaining functional symbiosis.
  3. Prey has little effect on the outcome of competition.
  4. The inferior competitor is lost more slowly when light is intermediate.
  5. The amount of symbiont present affects the rate of its competitive exclusion (i.e. log(tolerant/sensitive) vs time is not linear).


# Simulate competition

```{r set-pars, cache=TRUE}
  #### Set parameters ####

  # Parameters for determining outcome of symbiont competition. Initialize the symbionts as a
  # 50-50 mix. Here sensitive symbiont is symbiont 1; tolerant is symbiont 2
  pars_competition <- def_pars(nsym=2)
  pars_competition$jCPm[2] <- 1.0
  pars_competition$kROS[2] <- 250
  pars_competition$jSGm[2] <- 0.15
  pars_competition$initS[1:2] <- c(0.5, 0.5)


  # To determine how quickly the tolerant symbiont is lost, we set
  # the sensitive symbiont to symbiont 1 and the tolerant to symbiont 2 and
  # initialize the tolerant symbiont at 99% of the total symbionts
  pars_tol_exclusion <- def_pars(nsym=2)
  pars_tol_exclusion$jCPm[2] <- 1.0
  pars_tol_exclusion$kROS[2] <- 250
  pars_tol_exclusion$jSGm[2] <- 0.15
  pars_tol_exclusion$initS[1:2] <- c(0.01, 0.99)

  # To determine how quickly the sensitive symbiont is lost, we set
  # the tolerant symbiont to symbiont 1 and initialize the sensitive symbiont
  # at 99% of the total symbionts
  pars_sen_exclusion <- def_pars(nsym=2)
  pars_sen_exclusion$jCPm[1] <- 1.0
  pars_sen_exclusion$kROS[1] <- 250
  pars_sen_exclusion$jSGm[1] <- 0.15
  pars_sen_exclusion$initS[1:2] <- c(0.01, 0.99)

  # Randomly draw the environmental parameters
  env_params <- data.frame("L"=runif(20000, 5, 60), # Light, choose values between 5 and 60 mol photons/m^2/d
                              "N"=runif(20000, 1e-8, 1e-5), # DIN, choose values between 1e-8 and 1e-5 mol/L
                              "X" = runif(20000, 0, 4e-7)) # Food, choose values between 0 and 4e-7 mol/L

  # Parameters for symbiont competitive exclusion simulations
  threshold <- 0.01/0.99 # Calculate how long it takes for the symbiont to decline to 1% of the total symbionts
  max_time <- 365*20 # Give up if threshold has not been reached after 20 years
  dt <- 0.1 # Simulate taking time steps of 0.1 day
```


```{r run-competition-sims, cache=TRUE, dependson=c("set-pars")}
  #### Determine the outcome of symbiont competition under various environmental conditions ####

  # Run simulations for 10 years
  time<-seq(0, 10*365, 0.1)

  # Set up to run simulations in parallel
  cl <- makeCluster(detectCores() - 1)
  registerDoParallel(cl)


  # results will temporarily hold the summary statistics from the simulations
  results <- foreach(i=1:nrow(env_params), .combine='rbind', .packages='dplyr') %dopar% {

    # Set up the environmental conditions
    env <- coRal::init_env(time=time, L=c(env_params[i, "L"], env_params[i, "L"], 0),
      N=c(env_params[i, "N"], env_params[i, "N"], 0), X=c(env_params[i, "X"], env_params[i, "X"], 0))

    # Run the simulation
    run <- coRal::run_coral(time=time, env=env, pars=pars_competition)

    # Calculate C-N limitation
    cnlim <- cn_limitation(run, pars_competition)

    # Possible measures of host healthy and functional symbiosis:
    #host growth, lack of carbon limitation
    posGrH <- (run$dH.Hdt[length(time)] > 0) # Is host growth positive?
    noClimH <- (cnlim$H[length(time)] >= 0) # Is host NOT carbon-limited?
    noClimS.1 <- (cnlim$S.1[length(time)] >= 0) # Is the sensitive symb. NOT carbon-limited?
    noClimS.2 <- (cnlim$S.2[length(time)] >= 0) # Is the tolerant symb. NOT carbon-limited?
    noClimAll <- noClimH & noClimS.1 & noClimS.2 # Are parties NOT carbon-limited?

    # Which symbiont is the superior competitor?
    logTS <- log(run$S.2[length(time)]) - log(run$S.1[length(time)]) # log sensitive:tolerant ratio
    grS.1 <- run$dS.Sdt.1[length(time)] # Sensitive symb. per capita growth rate
    grS.2 <- run$dS.Sdt.2[length(time)] # Tolerant symb. per capita growth rate

    if(posGrH) { #& noClimAll) {
        if(logTS > 0) {
          sup_competitor <- "Tolerant" # There are more tolerant than sensitive symbionts
        } else if(logTS < 0) {
          sup_competitor <- "Sensitive" # More sensitive than tolerant symbionts
        } else if(logTS == 0) {
          sup_competitor <- "Equal-competitors" # Equal amounts of symbionts
        } else {
          sup_competitor <- NA # if logTS is not a number, something's gone wrong
        }
    } else {
      sup_competitor <- "No-survival" # The host is dead so symbiont competition doesn't matter
    }

    # Return the environmental parameters, survival and competition information
    list("L"=env_params[i, "L"], "N"=env_params[i, "N"], "X"=env_params[i, "X"],
      "posGrH"=posGrH, "noClimAll"=noClimAll, "logTS"=logTS,
      "grS.1"=grS.1, "grS.2"=grS.2, "sup_competitor"=sup_competitor)
  }

  # Stop the cluster
  stopCluster(cl)

  # Store results in dataframe, set column types
  sim_competition <- data.frame(results, row.names=NULL)
  sim_competition <- transform(sim_competition, L=as.numeric(L), N=as.numeric(N), X=as.numeric(X),
    posGrH=as.logical(posGrH), noClimAll=as.logical(noClimAll), logTS=as.numeric(logTS),
    grS.1=as.numeric(grS.1), grS.2=as.numeric(grS.2),
    sup_competitor=factor(sup_competitor, levels=c("Sensitive", "Tolerant", "No-survival", "Equal-competitors")))
```


```{r run-tolerant-exclusion-sims, cache=TRUE, dependson=c("set-pars", "run-competition-sims")}
  #### Simulate the competitive exclusion of the tolerant symbiont ####

  # Get the environments where the tolerant symbiont should be lost over time
  env_tol_exclusion <- sim_competition[sim_competition$sup_competitor == "Sensitive", c("L", "N", "X")]

  # Set up to run simulations in parallel
  cl <- makeCluster(detectCores() - 1)
  registerDoParallel(cl)

  # Results will temporarily hold the summary statistics from the simulations
  results <- foreach(i=1:nrow(env_tol_exclusion), .combine='rbind', .packages='dplyr') %dopar% {

    # Set up the environmental conditions
    env <- list(L=env_tol_exclusion[i, "L"], N=env_tol_exclusion[i, "N"], X=env_tol_exclusion[i, "X"])

    # Run the simulation
    run <- run_coral_comp_exclusion(env=env, pars=pars_tol_exclusion, max_time=max_time, dt=dt, threshold=threshold)

    # Was the threshold tolerant:sensitive ratio reached?
    reachedThreshold <- run$reachedThreshold

    # If so, when was the threshold reached?
    if(reachedThreshold) {
      exclusionTime <- run$fluxes$time[length(run$fluxes$time)]
    } else {
      exclusionTime <- NA
    }

    # Check that the host is alive
    cnlim <- cn_limitation(run$fluxes, pars_tol_exclusion) # Calculate carbon/nitrogen limitation
    posGrH <- (run$fluxes$dH.Hdt[length(run$fluxes$dH.Hdt)] > 0) # Is the host growing?
    noClimH <- (cnlim$H[length(time)] >= 0) # Is host NOT carbon-limited?
    noClimS.1 <- (cnlim$S.1[length(time)] >= 0) # Is the sensitive symb. NOT carbon-limited?
    noClimS.2 <- (cnlim$S.2[length(time)] >= 0) # Is the tolerant symb. NOT carbon-limited?
    noClimAll <- noClimH & noClimS.1 & noClimS.2 # Are parties NOT carbon-limited?

    # Check that host was alive at 100 days post-initialization
    time <- seq(0, 100, 0.1)
    env <- coRal::init_env(time, L=c(env_tol_exclusion[i, "L"], env_tol_exclusion[i, "L"], 0),
      N=c(env_tol_exclusion[i, "N"], env_tol_exclusion[i, "N"], 0), X=c(env_tol_exclusion[i, "X"], env_tol_exclusion[i, "X"], 0))

    run_survival <- coRal::run_coral(time=time, env=env, pars=pars_tol_exclusion)

    cnlim100d <- cn_limitation(run_survival, pars_tol_exclusion) # Calculate carbon/nitrogen limitation
    posGrH100d <- (run_survival$dH.Hdt[length(time)] > 0) # Is the host growing?
    noClimH100d <- (cnlim100d$H[length(time)] >= 0) # Is host NOT carbon-limited?
    noClimS100d.1 <- (cnlim100d$S.1[length(time)] >= 0) # Is the sensitive symb. NOT carbon-limited?
    noClimS100d.2 <- (cnlim100d$S.2[length(time)] >= 0) # Is the tolerant symb. NOT carbon-limited?
    noClimAll100d <- noClimH100d & noClimS100d.1 & noClimS100d.2 # Are parties NOT carbon-limited?

    # Return environmental parameters, whether the threshold was reached, and, if so, when
    list("L"=env_tol_exclusion[i, "L"], "N"=env_tol_exclusion[i, "N"], "X"=env_tol_exclusion[i, "X"],
      "reachedThreshold"=reachedThreshold, "exclusionTime"=exclusionTime, "posGrH"=posGrH,
      "noClimAll"=noClimAll, "posGrH100d"=posGrH100d, "noClimAll100d"=noClimAll100d)
  }

  # Stop the cluster
  stopCluster(cl)

  # Store results in dataframe, set column types
  sim_tol_exclusion <- data.frame(results, row.names=NULL)
  sim_tol_exclusion <- transform(sim_tol_exclusion, L=as.numeric(L), N=as.numeric(N), X=as.numeric(X),
    reachedThreshold=as.logical(reachedThreshold), exclusionTime=as.numeric(exclusionTime),
    posGrH=as.logical(posGrH), noClimAll=as.logical(noClimAll),
    posGrH100d=as.logical(posGrH100d), noClimAll100d=as.logical(noClimAll100d))
```


```{r run-sensitive-exclusion-sims, cache=TRUE, dependson=c("set-pars", "run-competition-sims")}
  #### Simulate the competitive exclusion of the sensitive symbiont ####

  # Get the environments where the sensitive symbiont should be lost over time
  env_sen_exclusion <- sim_competition[sim_competition$sup_competitor == "Tolerant", c("L", "N", "X")]

  # Set up to run simulations in parallel
  cl <- makeCluster(detectCores() - 1)
  registerDoParallel(cl)

  # Results will temporarily hold the summary statistics from the simulations
  results <- foreach(i=1:nrow(env_sen_exclusion), .combine='rbind', .packages='dplyr') %dopar% {

    # Set up the environmental conditions
    env <- list(L=env_sen_exclusion[i, "L"], N=env_sen_exclusion[i, "N"], X=env_sen_exclusion[i, "X"])

    # Run the simulation
    run <- run_coral_comp_exclusion(env=env, pars=pars_sen_exclusion, max_time=max_time, dt=dt, threshold=threshold)

    # Was the threshold tolerant:sensitive ratio reached?
    reachedThreshold <- run$reachedThreshold

    # If so, when was the threshold reached?
    if(reachedThreshold) {
      exclusionTime <- run$fluxes$time[length(run$fluxes$time)]
    } else {
      exclusionTime <- NA
    }

    # Check that the host is alive
    cnlim <- cn_limitation(run$fluxes, pars_sen_exclusion) # Calculate carbon/nitrogen limitation
    posGrH <- (run$fluxes$dH.Hdt[length(run$fluxes$dH.Hdt)] > 0) # Is the host growing?
    noClimH <- (cnlim$H[length(time)] >= 0) # Is host NOT carbon-limited?
    noClimS.1 <- (cnlim$S.1[length(time)] >= 0) # Is the sensitive symb. NOT carbon-limited?
    noClimS.2 <- (cnlim$S.2[length(time)] >= 0) # Is the tolerant symb. NOT carbon-limited?
    noClimAll <- noClimH & noClimS.1 & noClimS.2 # Are parties NOT carbon-limited?

    # Check that host was alive at 100 days post-initialization
    time <- seq(0, 100, 0.1)
    env <- coRal::init_env(time, L=c(env_sen_exclusion[i, "L"], env_sen_exclusion[i, "L"], 0),
      N=c(env_sen_exclusion[i, "N"], env_sen_exclusion[i, "N"], 0), X=c(env_sen_exclusion[i, "X"], env_sen_exclusion[i, "X"], 0))

    run_survival <- coRal::run_coral(time=time, env=env, pars=pars_sen_exclusion)

    cnlim100d <- cn_limitation(run_survival, pars_sen_exclusion) # Calculate carbon/nitrogen limitation
    posGrH100d <- (run_survival$dH.Hdt[length(time)] > 0) # Is the host growing?
    noClimH100d <- (cnlim100d$H[length(time)] >= 0) # Is host NOT carbon-limited?
    noClimS100d.1 <- (cnlim100d$S.1[length(time)] >= 0) # Is the sensitive symb. NOT carbon-limited?
    noClimS100d.2 <- (cnlim100d$S.2[length(time)] >= 0) # Is the tolerant symb. NOT carbon-limited?
    noClimAll100d <- noClimH100d & noClimS100d.1 & noClimS100d.2 # Are parties NOT carbon-limited?

    # Return environmental parameters, whether the threshold was reached, and, if so, when
    list("L"=env_sen_exclusion[i, "L"], "N"=env_sen_exclusion[i, "N"], "X"=env_sen_exclusion[i, "X"],
      "reachedThreshold"=reachedThreshold, "exclusionTime"=exclusionTime, "posGrH"=posGrH,
      "noClimAll"=noClimAll, "posGrH100d"=posGrH100d, "noClimAll100d"=noClimAll100d)
  }

  # Stop the cluster
  stopCluster(cl)

  # Store results in dataframe, set column types
  sim_sen_exclusion <- data.frame(results, row.names=NULL)
  sim_sen_exclusion <- transform(sim_sen_exclusion, L=as.numeric(L), N=as.numeric(N), X=as.numeric(X),
    reachedThreshold=as.logical(reachedThreshold), exclusionTime=as.numeric(exclusionTime),
    posGrH=as.logical(posGrH), noClimAll=as.logical(noClimAll),
    posGrH100d=as.logical(posGrH100d), noClimAll100d=as.logical(noClimAll100d))
```

# Where is each symbiont competitively dominant?

```{r plot-symb-competition, cache=TRUE, dependson=c("run-competition-sims"), fig.width=10, fig.height=5}
  #### Linear discriminant analysis ####

  # Center and scale the environmental variables
  datalda <- sim_competition[, c("sup_competitor", "L", "N", "X")]
  datalda$L <- (datalda$L - mean(datalda$L))/sd(datalda$L)
  datalda$N <- (datalda$N - mean(datalda$N))/sd(datalda$N)
  datalda$X <- (datalda$X - mean(datalda$X))/sd(datalda$X)

  # Run the linear discriminant analysis
  outlda <- lda(sup_competitor ~ L + N + X, datalda)

  # Plot the data on the linear discriminant axes
  pdf("competitive_dominance.pdf", 10, 5)
  layout(matrix(c(1, 1, 2, 3, 1, 1, 4, 5), nrow=2, byrow=TRUE), respect=TRUE)

  plot(predict(outlda)$x[,1], predict(outlda)$x[,2],
    col=c(transparent(colSen, 0.25), transparent(colTol, 0.25), transparent(colNS, 0.25))[datalda$sup_competitor],
  	pch=c(pchSen, pchTol, pchNS)[datalda$sup_competitor],
    xlab="LD 1", ylab="LD 2", main="(a) Linear discriminant analysis")

  # Add arrows representing the environmental variables in LD space
  arrows(x0=0, y0=0, x1=1.5*outlda$scaling[1,1], y1=1.5*outlda$scaling[1,2], length=0.1, col="white", lwd=5)
  arrows(x0=0, y0=0, x1=1.5*outlda$scaling[1,1], y1=1.5*outlda$scaling[1,2], length=0.1, col="black", lwd=2)
  rect(xleft=1.25*outlda$scaling[1,1] - strwidth("Light")/2 - 0.1, ybottom=1.25*outlda$scaling[1,2] - 0.5*strheight("Light") + 0.15,
    xright=1.25*outlda$scaling[1,1] + strwidth("Light")/2 + 0.1, ytop=1.25*outlda$scaling[1,2] + 0.5*strheight("Light") + 0.35,
    col="white", border=NA)
  text(x=1.25*outlda$scaling[1,1], y=1.25*outlda$scaling[1,2] + 0.25, labels="Light", col="black")

  arrows(x0=0, y0=0, x1=1.5*outlda$scaling[2,1], y1=1.5*outlda$scaling[2,2], length=0.1, col="white", lwd=5)
  arrows(x0=0, y0=0, x1=1.5*outlda$scaling[2,1], y1=1.5*outlda$scaling[2,2], length=0.1, col="black", lwd=2)
  rect(xleft=1.25*outlda$scaling[2,1] - strwidth("Nitrogen") - 0.35, ybottom=1.25*outlda$scaling[2,2] - 0.5*strheight("Nitrogen") - 0.1,
    xright=1.25*outlda$scaling[2,1] - 0.15, ytop=1.25*outlda$scaling[2,2] + 0.5*strheight("Nitrogen") + 0.1,
    col="white", border=NA)
  text(x=1.25*outlda$scaling[2,1] - 0.25, y=1.25*outlda$scaling[2,2], adj=1, labels="Nitrogen", col="black")

  arrows(x0=0, y0=0, x1=1.5*outlda$scaling[3,1], y1=1.5*outlda$scaling[3,2], length=0.1, col="white", lwd=5)
  arrows(x0=0, y0=0, x1=1.5*outlda$scaling[3,1], y1=1.5*outlda$scaling[3,2], length=0.1, col="black", lwd=2)
  rect(xleft=1.25*outlda$scaling[3,1] - strwidth("Prey") - 0.35, ybottom=1.25*outlda$scaling[3,2] - 0.5*strheight("Prey") - 0.1,
    xright=1.25*outlda$scaling[3,1] - 0.15, ytop=1.25*outlda$scaling[3,2] + 0.5*strheight("Prey") + 0.1,
    col="white", border=NA)
  text(x=1.25*outlda$scaling[3,1] - 0.25, y=1.25*outlda$scaling[3,2], adj=1, labels="Prey", col="black")

  #### Plot competition outcome vs each environmental variable ####

  evenBarsHist(data=list(sim_competition$L[(sim_competition$sup_competitor == "Sensitive")],
    sim_competition$L[(sim_competition$sup_competitor == "Tolerant")],
    sim_competition$L[(sim_competition$sup_competitor == "No-survival")]),
    breaks=seq(5, 60, 2.5), xlim=c(5, 60), colors=c(colSen, colTol, colNS),
    xlab="Light (mol photons/m^2/day)", ylab="% Simulations", main="(b) Light")


  evenBarsHist(data=list(sim_competition$N[(sim_competition$sup_competitor == "Sensitive")],
    sim_competition$N[(sim_competition$sup_competitor == "Tolerant")],
    sim_competition$N[(sim_competition$sup_competitor == "No-survival")]),
    colors=c(colSen, colTol, colNS),
    xlab="Nitrogen (mol/L)", ylab="% Simulations", main="(c) Nitrogen")

  evenBarsHist(data=list(sim_competition$X[(sim_competition$sup_competitor == "Sensitive")],
    sim_competition$X[(sim_competition$sup_competitor == "Tolerant")],
    sim_competition$X[(sim_competition$sup_competitor == "No-survival")]),
    colors=c(colSen, colTol, colNS),
    xlab="Prey (mol/L)", ylab="% Simulations", main="(d) Prey")

  # Legend
  par(mar=c(0,0,0,0))
  plot.new()
  legend("center", c("Sensitive symb.", "Tolerant symb.", "No survival"),
  	col=c(colSen, colTol, colNS), pch=c(pchSen, pchTol, pchNS),
  	title="Superior competitor", cex=1.3, pt.cex=1.5)
  dev.off()

  # Print the results of the linear discriminant analysis
  outlda
```


# How do environmental variables affect the time to competitive exclusion?

```{r plot-light-nitrogen-vs-exclusion, cache=TRUE, dependson=c("run-tolerant-exclusion-sims", "run-sensitive-exclusion-sims")}
  pdf("competitive_exclusion.pdf", 12, 12)
  layout(matrix(c(1, 2), nrow=2, byrow=TRUE), respect=FALSE)
  ## Light

  plot(sim_tol_exclusion$L[sim_tol_exclusion$reachedThreshold & sim_tol_exclusion$posGrH100d], #& sim_tol_exclusion$noClimAll100d],
  	sim_tol_exclusion$exclusionTime[sim_tol_exclusion$reachedThreshold  & sim_tol_exclusion$posGrH100d]/365, #& sim_tol_exclusion$noClimAll100d]/365,
    xlim=c(5, 60), ylim=c(1/365, 20+1), xlab="Light (mol photons/m^2/day)",
  	ylab="Time to competitive exclusion (years)", col=colTol, pch=pchTol,
  	main="(a) Light")

  points(sim_sen_exclusion$L[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH100d], #& sim_sen_exclusion$noClimAll100d],
  	sim_sen_exclusion$exclusionTime[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH100d]/365, #& sim_sen_exclusion$noClimAll100d]/365,
  	col=colSen, pch=pchSen)

  points(sim_tol_exclusion$L[!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH100d], #& sim_tol_exclusion$noClimAll100d],
  	rep(21, sum(!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH100d)), #& sim_tol_exclusion$noClimAll100d)),
  	col=colTol, pch=17)

  points(sim_sen_exclusion$L[!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH100d], #& sim_sen_exclusion$noClimAll100d],
  	rep(21, sum(!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH100d)), #& sim_sen_exclusion$noClimAll100d)),
  	col=colSen, pch=2)

  legend("topright", c("Exclusion of tol.", "Exclusion of tol. takes > 20 yrs", "Exclusion of sen.", "Exclusion of sen. takes > 20 yrs"),
  	pch=c(pchTol, 17, pchSen, 2), col=c(colTol, colTol, colSen, colSen), pt.bg=c("white", rgb(0, 0, 1, 0.25)))


  ## Nitrogen

  plot(sim_tol_exclusion$N[sim_tol_exclusion$reachedThreshold& sim_tol_exclusion$posGrH100d], #& sim_tol_exclusion$noClimAll100d],
  	sim_tol_exclusion$exclusionTime[sim_tol_exclusion$reachedThreshold & sim_tol_exclusion$posGrH100d]/365, #& sim_tol_exclusion$noClimAll100d]/365,
    xlim=c(1e-8, 1e-5), ylim=c(1/365, 20+1), xlab="Nitrogen (mol/L)", log="x", # Plot on log scale to better what's happening at low N, where the interesting stuff is
  	ylab="Time to competitive exclusion (years)", col=colTol, pch=pchTol,
  	main="(b) Nitrogen")

  points(sim_sen_exclusion$N[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH100d], #& sim_sen_exclusion$noClimAll100d],
  	sim_sen_exclusion$exclusionTime[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH100d]/365, #& sim_sen_exclusion$noClimAll100d]/365,
  	col=colSen, pch=pchSen)

  points(sim_tol_exclusion$N[!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH100d], #& sim_tol_exclusion$noClimAll100d],
  	rep(21, sum(!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH100d)), #& sim_tol_exclusion$noClimAll100d)),
  	col=colTol, pch=17)

  points(sim_sen_exclusion$N[!(sim_sen_exclusion$reachedThreshold)& sim_sen_exclusion$posGrH100d], #& sim_sen_exclusion$noClimAll100d],
  	rep(21, sum(!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH100d)), #& sim_sen_exclusion$noClimAll100d)),
  	col=colSen, pch=2)

  dev.off()
```


```{r plot-food-vs-exclusion, cache=TRUE, dependson=c("run-tolerant-exclusion-sims", "run-sensitive-exclusion-sims")}
  ## Food

  pdf("competitive_exclusion_prey.pdf", 6, 6)

  layout(matrix(c(1, 2), nrow=2, byrow=TRUE), respect=FALSE, heights=c(0.75, 0.25))

  plot(sim_tol_exclusion$X[sim_tol_exclusion$reachedThreshold& sim_tol_exclusion$posGrH100d], #& sim_tol_exclusion$noClimAll100d],
  	sim_tol_exclusion$exclusionTime[sim_tol_exclusion$reachedThreshold & sim_tol_exclusion$posGrH100d]/365, #& sim_tol_exclusion$noClimAll100d]/365,
  	xlim=c(0, 4e-7), ylim=c(1/365, 20+1), xlab="Prey (mol/L)",
  	ylab="Time (years)", col=colTol, pch=pchTol,
  	main="Prey vs. time to competitive exclusion")

  points(sim_sen_exclusion$X[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH100d], #& sim_sen_exclusion$noClimAll100d],
  	sim_sen_exclusion$exclusionTime[sim_sen_exclusion$reachedThreshold & sim_sen_exclusion$posGrH100d]/365, #& sim_sen_exclusion$noClimAll100d]/365,
  	col=colSen, pch=pchSen)

  points(sim_tol_exclusion$X[!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH100d], #& sim_tol_exclusion$noClimAll100d],
  	rep(21, sum(!(sim_tol_exclusion$reachedThreshold) & sim_tol_exclusion$posGrH100d)), #& sim_tol_exclusion$noClimAll100d)),
  	col=colTol, pch=17)

  points(sim_sen_exclusion$X[!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH100d], #& sim_sen_exclusion$noClimAll100d],
  	rep(21, sum(!(sim_sen_exclusion$reachedThreshold) & sim_sen_exclusion$posGrH100d)), #& sim_sen_exclusion$noClimAll100d)),
  	col=colSen, pch=2)


  ## Legend
  par(mar=c(0, 0, 0, 0))
  plot.new()

  legend("center", c("Exclusion of tol.", "Exclusion of tol. takes > 20 yrs", "Exclusion of sen.", "Exclusion of sen. takes > 20 yrs"),
  	pch=c(pchTol, 17, pchSen, 2), col=c(colTol, colTol, colSen, colSen), pt.bg=c("white", rgb(0, 0, 1, 0.25)))

  dev.off()
```


```{r summary-statistics, cache=TRUE, dependson=c("run-tolerant-exclusion-sims", "run-sensitive-exclusion-sims")}
  summary(sim_tol_exclusion[sim_tol_exclusion$posGrH100d,]) #& sim_tol_exclusion$noClimAll100d,])

  summary(sim_sen_exclusion[sim_sen_exclusion$posGrH100d,]) #& sim_sen_exclusion$noClimAll100d,])
```

# What do the dynamics of competitive exclusion look like?

```{r plot-exclusion-dynamics, cache=TRUE, dependson=c("set-pars", "run-tolerant-exclusion-sims", "run-sensitive-exclusion-sims")}
  time <- seq(0, 2*365)

  par(mfrow=c(4,3))
  for(i in 1:4) {
    Li <- sim_tol_exclusion[i, "L"]
    Ni <- sim_tol_exclusion[i, "N"]
    Xi <- sim_tol_exclusion[i, "X"]

    env <- init_env(time=time, L=c(Li, Li, 0), N=c(Ni, Ni, 0), X=c(Xi, Xi, 0))

    run <- coRal::run_coral(time=time, env=env, pars=pars_tol_exclusion)
    run2 <- coRal::run_coral(time=time, env=env, pars=pars_competition)

    minSH <- min(run$S.1/run$H, run$S.2/run$H)
    maxSH <- max(run$S.1/run$H, run$S.2/run$H)

    plot(time, run$S.1/run$H, type="l", col=colSen, xlab="time (days)", ylab="S/H ratio",
      main=paste("Sim", i), ylim=c(minSH, maxSH), log="y")
    lines(time, run$S.2/run$H, col=colTol)

    minSH <- min(run2$S.1/run2$H, run2$S.2/run2$H)
    maxSH <- max(run2$S.1/run2$H, run2$S.2/run2$H)

    plot(time, run2$S.1/run2$H, type="l", col=colSen, xlab="time (days)", ylab="S/H ratio",
      main=paste("Sim", i), ylim=c(minSH, maxSH), log="y")
    lines(time, run2$S.2/run2$H, col=colTol)

    minGr <- min(c(run$dH.Hdt[-1], run2$dH.Hdt[-1]))
    maxGr <- max(c(run$dH.Hdt[-1], run2$dH.Hdt[-1]))

    plot(time[-1], run$dH.Hdt[-1], col="gray", type="l", lwd=2, xlab="time (days)",
    ylab="Host growth rate", main=paste("Sim", i), ylim=c(minGr, maxGr))

    lines(time[-1], run2$dH.Hdt[-1], col="black")
  }
```
